---
title: "5th Sentinel process"
author: "Zhehan Tang"
date: "January 17, 2018"
output: html_document
---

#package preparation
```{r}
library(dplyr)
library(raster)
```

#read swp data
```{r}
path_swp <- "G:/CITRIS Project/Walnut_SWP"

swp_5theast_2016 <- na.omit(read.csv(file.path(path_swp, "2016 5th east walnut swp.csv"),header = TRUE)[,c(1,3,4,5)])
swp_5theast_2017 <- na.omit(read.csv(file.path(path_swp, "2017 5th east walnut swp.csv"),header = TRUE)[,c(1,3,4,5)])
swp_5thwest_2016 <- na.omit(read.csv(file.path(path_swp, "2016 5th west walnut swp.csv"),header = TRUE)[,c(1,3,4,5)])
swp_5thwest_2017 <- na.omit(read.csv(file.path(path_swp, "2017 5th west walnut swp.csv"),header = TRUE)[,c(1,3,4,5)])

#change date format
swp_5theast_2016$Date <- as.Date.character(swp_5theast_2016$Date, format = "%d-%b-%y")
swp_5theast_2017$Date <- as.Date.character(swp_5theast_2017$Date, format = "%d-%b-%y")
swp_5thwest_2016$Date <- as.Date.character(swp_5thwest_2016$Date, format = "%d-%b-%y")
swp_5thwest_2017$Date <- as.Date.character(swp_5thwest_2017$Date, format = "%d-%b-%y")

```

#histogram of the swp distribution 
```{r}
par(mfrow=c(2,2))
hist(swp_5theast_2016$Avg)
hist(swp_5thwest_2016$Avg)
hist(swp_5theast_2017$Avg)
hist(swp_5thwest_2017$Avg)
```

#Read sentinel data of 5th walnut site

##function to read sentinel
```{r}
read_sentinel <- function(path, sentinel_image){
  #sentinel_image is the name of the sentinel file

  #get the brick
  sentinel <- brick(file.path(path, sentinel_image))
  
  #spectral subset for 10 bands
  require(raster)
  sentinel <- raster::subset(sentinel, 1:10)
  
  #rename the bands 
  names(sentinel) <- c('blue', 'green', 'red', 'rededge1', 'rededge2', 'rededge3', 'nir', 'rededge4', 'swir1', 'swir2')
  
  #output
  return(sentinel)
}
```

##Read the sentinel of match dates 
```{r}
path_wal_sen <- "G:/CITRIS Project/Walnut_sentinel"

sen_5th_20170704 <- read_sentinel(path_wal_sen, "20170704_5th_10m_nearest.tif")
sen_5th_20170915 <- read_sentinel(path_wal_sen, "20170915_5th_10m_nearest.tif")
sen_5th_20170922 <- read_sentinel(path_wal_sen, "20170922_5th_10m_nearest.tif")
sen_5th_20171017 <- read_sentinel(path_wal_sen, "20171017_5th_10m_nearest.tif")

sen_5th_list <- list("20170704"=sen_5th_20170704, "20170915"=sen_5th_20170915, "20170922"=sen_5th_20170922, "20171017"=sen_5th_20171017)
```

#Read the shapefile of site boundary and swp tree
```{r}
path_boundary <- "G:/CITRIS Project/site locations/Shapefiles"
boundary_5th <- shapefile(file.path(path_boundary, "5th_walnut_boundary.shp"))
tree_5th <- shapefile(file.path(path_boundary,"5th_walnut.shp"))

#unify the crs
boundary_5th <- spTransform(boundary_5th, crs(sen_5th_20170704))
tree_5th <- spTransform(tree_5th, crs(sen_5th_20170704))

#change the name of shapefiles
boundary_5th$Name = "5th_walnut"

#remove extra dimension of coordinate system
tree_5th@coords <- tree_5th@coords[,1:2]

#subset the east and west tree
east_5th <- tree_5th[tree_5th$Name=="5th east",]
west_5th <- tree_5th[tree_5th$Name=="5th west",]
east_5th$Name <- "5th_east"
west_5th$Name <- "5th_west"

dev.off()
plotRGB(sen_5th_20170704, 3,2,1, stretch="lin")
plot(boundary_5th, add = TRUE, col="white")
plot(east_5th, add = TRUE, col="black")
plot(west_5th, add = TRUE, col="red")
dev.off()
```


# The function to extract values of the trees 
- Also test two different extract methods: simple and bilinear. If 'simple' values for the cell a point falls in are returned. If 'bilinear' the returned values are interpolated from the values of the four nearest raster cells.
```{r}
extract_sen <- function(sentinel_list, locations, method, fun){
  #sentinel_list: it is the list to store all sentinel rasterbrick
  #locations: it has 3 options: wal_blocks, wal_centers, wal_points, wal_field
  #method: it is the method used in the extract function. it has 2 optiosn: 'simple' or 'bilinear'
  #fun: it is the fun in the extract function, determining how to summarize the values. Usually it's either mean or median
  #buffer: it is the buffer in the extract function, determining the radius. Don't use when it's MAP2_blocks.  
  
  #this is the list to store all the produced data frame for each date
  extract_sentinel_list <- list()
  
  #In the for loop, every sublist stores a data frame extracted from the sentinel image of that date
  for(i in 1:length(sentinel_list)){
    extract_sentinel_list[[i]]<- raster::extract(x = sentinel_list[[i]], y = locations, method, fun, df = TRUE, na.rm=TRUE, buffer = NULL)
    extract_sentinel_list[[i]]$ID <- locations$Name
  }
  
  #give names (corresponding dates) to the list
  names(extract_sentinel_list) <- names(sentinel_list)
  return(extract_sentinel_list)
}

```

#Extract reflectance values of the locations
```{r}
walsen_5th_sim <- extract_sen(sen_5th_list, tree_5th, method="simple", fun = mean)
```

#Vegetation indices functions
```{r}
ndvi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(ndvi)
}
grvi1 <- function(sentinel){
  band_red <- sentinel$red
  band_green <- sentinel$green
  grvi1 <- (band_red - band_green)/(band_red + band_green)
  return(grvi1)
}
gndvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  gndvi <- (band_842 - band_560)/(band_842 + band_560)
  return(gndvi)
}
sr <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  sr <- band_nir/band_red
  return(sr)
}
gci <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  gci <- band_nir/band_green
}
sr.green <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  sr.green <- band_842/band_560
  return(sr.green)
}
cvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  band_665 <- sentinel$red
  cvi <- (band_842/band_560)/(band_560+band_665)
  return(cvi)
}
savi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  savi <- 1.5*(band_nir-band_red)/(band_nir+band_red+0.5)
  return(savi)
}
psri.nir <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_nir <- sentinel$nir
  psri.nir <- (band_red - band_blue)/(band_nir)
  return(psri.nir)
}
ndvi.green <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  ndvi.green <- band_green*(band_nir - band_red)/(band_nir + band_red)
  return(ndvi.green)
}
msavi2 <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  msavi2 <- (band_nir + 1) - 0.5*sqrt((2*band_nir - 1)^2 + 8*band_red)
  return(msavi2)
}
lai.savi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  lai.savi <- -log(0.371 + 1.5*(band_nir - band_red)/(band_nir + band_red + 0.5))/2.4
  return(lai.savi)
}
cri1 <- function(sentinel){
  band_green <- sentinel$green
  band_blue <- sentinel$blue
  cri1 <- (1/band_blue)-(1/band_green)
  return(cri1)
}
arvi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  arvi <- (band_nir - (2*band_red - band_blue))/(band_nir + (2*band_red-band_blue))
  return(arvi)
}
ari2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_blue <- sentinel$blue
  band_green <- sentinel$green
  ari2 <- (band_nir/band_blue)-(band_nir/band_green)
  return(ari2)
}
ndwi <- function(sentinel){
  band_swir1 <- sentinel$swir1
  band_nir <- sentinel$nir
  ndwi <- (band_nir - band_swir1)/(band_swir1 + band_nir)
  return(ndwi)
}
re.ndwi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  re.ndwi <- (band_green-band_rededge1)/(band_green+band_rededge1)
  return(re.ndwi)
}
re.ndvi.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  return(re.ndvi.1)
}
re.ndvi.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  return(re.ndvi.2)
}
re.ndvi.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  return(re.ndvi.3)
}
psri <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  psri <- (band_red - band_blue)/(band_rededge1)
  return(psri)
}
ndre.1 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_740 <- sentinel$rededge2
  ndre.1 <- (band_740-band_705)/(band_740+band_705)
  return(ndre.1)
}
ndre.2 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_783 <- sentinel$rededge3
  ndre.2 <- (band_783-band_705)/(band_783+band_705)
  return(ndre.2)
}
ndre.3 <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_783 <- sentinel$rededge3
  ndre.3 <- (band_783-band_740)/(band_783+band_740)
  return(ndre.3)
}
ndi.45 <- function(sentinel){
  band_red <- sentinel$red 
  band_rededge1 <- sentinel$rededge1
  ndi.45 <- (band_rededge1-band_red)/(band_rededge1+band_red)
  return(ndi.45)
}
mtci <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  mtci <- (band_740-band_705)/(band_705-band_665)
  return(mtci)
}
msi <- function(sentinel){
  band_swir1 <- sentinel$swir1 
  band_nir <- sentinel$nir
  msi <- band_swir1/band_nir
  return(msi)
}
mcari <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  mcari <- 1-0.2*(band_rededge1 - band_green)/(band_rededge1 - band_red)
  return(mcari)
}
ireci <- function(sentinel){
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  band_rededge2 <- sentinel$rededge2
  band_rededge1 <- sentinel$rededge1
  ireci <- (band_rededge3 - band_red)*band_rededge2/band_rededge1
  return(ireci)
}
ci.rededge <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_705 <- sentinel$rededge1
  ci.rededge <- band_783/band_705 - 1
  return(ci.rededge)
}
ci.green <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_560 <- sentinel$green
  ci.green <- band_783/band_560 - 1
  return(ci.green)
}
cri2 <- function(sentinel){
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  cri2 <- (1/band_blue) - (1/band_rededge1)
  return(cri2)
}
chl.rededge.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  chl.rededge.1 <- band_nir/band_rededge1-1
  return(chl.rededge.1)
}
chl.rededge.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  chl.rededge.2 <- band_nir/band_rededge2-1
  return(chl.rededge.2)
}
chl.rededge.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  chl.rededge.3 <- band_nir/band_rededge3-1
  return(chl.rededge.3)
}
ari1 <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  ari1 <- (1/band_green)-(1/band_rededge1)
  return(ari1)
}
tcari.osavi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  
  tcari <- 3*((band_rededge1 - band_red)-0.2*(band_rededge1 - band_green)*band_rededge1/band_red)
  osavi <- (1+0.16)*(band_nir - band_red)/(band_nir + band_red + 0.16)
}
mcari.osavi <- function(sentinel){
  
  mcari <- (sentinel$rededge1 - sentinel$red) - 0.2*(sentinel$rededge1 - sentinel$green) * sentinel$rededge1/sentinel$red
  osavi <- (1+0.16)*(sentinel$nir-sentinel$red)/(sentinel$nir+sentinel$red+0.16)
  return(mcari/osavi)
}
mcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  mcari <- ((band_740-band_705)-0.2*(band_740-band_560))*band_740/band_705
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  return(mcari/osavi)
}
tcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  tcari <- 3*((band_740 - band_705) - 0.2*(band_740 - band_560)*band_740/band_705)
  return(tcari/osavi)
}
REP <- function(sentinel){
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  band_740 <- sentinel$rededge2
  band_783 <- sentinel$rededge3
  REP <- 705 + 35*((band_665 + band_783)/2-band_705)/(band_740-band_705)
  return(REP)
}
sccci.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.1/ndvi)
}
sccci.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  band_red <- sentinel$red
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.2/ndvi)
}
sccci.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.3/ndvi)
}

```

#NDVI for the entire field overtime
```{r}
walsen_5th_ndvi_list <- lapply(sen_5th_list, ndvi)

dev.off()
par(mfrow=c(2,2))
for(i in 1:4){
  hist(raster::mask(walsen_5th_ndvi_list[[i]],boundary_5th), main=paste(names(walsen_5th_ndvi_list)[i],"NDVI of the field"),xlab="")
}

par(mfrow=c(1,1))
sapply(walsen_5th_ndvi_list, function(x) extract(x,y=boundary_5th, fun=mean))
sapply(walsen_5th_ndvi_list, function(x) extract(x,y=boundary_5th, fun=median))

```

#The function to generate a data frame of reflectance and vegetation indices
```{r}
df_reflectance <- function(locations_method){

  for(i in 1:length(locations_method)){
    #change the value of reflectance (divided by 10000)
    locations_method[[i]][,-1] <- locations_method[[i]][-1]/10000
    
    #add new columns of vegetation indices
    ##ndvi
    locations_method[[i]]$ndvi <- ndvi(locations_method[[i]])
    #gci
    locations_method[[i]]$gci <- gci(locations_method[[i]])
    ##grvi1
    locations_method[[i]]$grvi1 <- grvi1(locations_method[[i]])
    ##gndvi
    locations_method[[i]]$gndvi <- gndvi(locations_method[[i]])
    ##sr
    locations_method[[i]]$sr <- sr(locations_method[[i]])
    ##sr.green
    locations_method[[i]]$sr.green <- sr.green(locations_method[[i]])
    ##cvi
    locations_method[[i]]$cvi <- cvi(locations_method[[i]])
    ##savi
    locations_method[[i]]$savi <- savi(locations_method[[i]])
    ##psri.nir
    locations_method[[i]]$psri.nir <- psri.nir(locations_method[[i]])
    ##ndvi.green
    locations_method[[i]]$ndvi.green <- ndvi.green(locations_method[[i]])
    ##msavi2
    locations_method[[i]]$msavi2 <- msavi2(locations_method[[i]])
    ##lai.savi
    locations_method[[i]]$lai.savi <- lai.savi(locations_method[[i]])
    ##cri
    locations_method[[i]]$cri1 <- cri1(locations_method[[i]])
    ##arvi
    locations_method[[i]]$arvi <- arvi(locations_method[[i]])
    ##ari2
    locations_method[[i]]$ari2 <- ari2(locations_method[[i]])
    ##ndwi
    locations_method[[i]]$ndwi <- ndwi(locations_method[[i]])
    ##re.ndwi
    locations_method[[i]]$re.ndwi <- re.ndwi(locations_method[[i]])
    ##re.ndvi.1
    locations_method[[i]]$re.ndvi.1 <- re.ndvi.1(locations_method[[i]])
    ##re.ndvi.2
    locations_method[[i]]$re.ndvi.2 <- re.ndvi.2(locations_method[[i]])
    ##re.ndvi.3
    locations_method[[i]]$re.ndvi.3 <- re.ndvi.3(locations_method[[i]])
    ##psri
    locations_method[[i]]$psri <- psri(locations_method[[i]])
    ##ndre.1
    locations_method[[i]]$ndre.1 <- ndre.1(locations_method[[i]])
    ##ndre.2
    locations_method[[i]]$ndre.2 <- ndre.2(locations_method[[i]])
    ##ndre.3
    locations_method[[i]]$ndre.3 <- ndre.3(locations_method[[i]])
    ##ndi.45
    locations_method[[i]]$ndi.45 <- ndi.45(locations_method[[i]])
    ##mtci
    locations_method[[i]]$mtci <- mtci(locations_method[[i]])
    ##msi
    locations_method[[i]]$msi <- msi(locations_method[[i]])
    ##mcari
    locations_method[[i]]$mcari <- mcari(locations_method[[i]])
    ##ireci
    locations_method[[i]]$ireci <- ireci(locations_method[[i]])
    ##ci.rededge
    locations_method[[i]]$ci.rededge <- ci.rededge(locations_method[[i]])
    ##ci.green
    locations_method[[i]]$ci.green <- ci.green(locations_method[[i]])
    ##cri2
    locations_method[[i]]$cri2 <- cri2(locations_method[[i]])
    ##chl.rededge.1
    locations_method[[i]]$chl.rededge.1 <- chl.rededge.1(locations_method[[i]])
    ##chl.rededge.2
    locations_method[[i]]$chl.rededge.2 <- chl.rededge.2(locations_method[[i]])
    ##chl.rededge.3
    locations_method[[i]]$chl.rededge.3 <- chl.rededge.3(locations_method[[i]])
    ##ari1
    locations_method[[i]]$ari1 <- ari1(locations_method[[i]])
    ##tcari.osavi
    locations_method[[i]]$tcari.osavi <- tcari.osavi(locations_method[[i]])
    ##mcari.osavi
    locations_method[[i]]$mcari.osavi <- mcari.osavi(locations_method[[i]])
    ##mcari.osavi.705
    locations_method[[i]]$mcari.osavi.705 <- mcari.osavi.705(locations_method[[i]])
    ##tcari.osavi.705
    locations_method[[i]]$tcari.osavi.705 <- tcari.osavi.705(locations_method[[i]])
    ##REP
    locations_method[[i]]$REP <- REP(locations_method[[i]])
    ##sccci.1
    locations_method[[i]]$sccci.1 <- sccci.1(locations_method[[i]])
    ##sccci.2
    locations_method[[i]]$sccci.2 <- sccci.2(locations_method[[i]])
    ##sccci.3
    locations_method[[i]]$sccci.3 <- sccci.3(locations_method[[i]])
  }
  names(locations_method) <- as.Date.character(names(locations_method), format = "%Y%m%d")
  return(locations_method)
}
```

#Use of df_reflectance function to calculate vegetation index
```{r}
df_walsen_5th_sim <- df_reflectance(walsen_5th_sim)
```

#integrate with swp data
```{r}

```

##integrate_swp function
```{r}
integrate_swp <- function(df_locations_method, locations){
  if (locations == "points"){
    locations_method_select <- list()
    for(i in 1:length(df_locations_method)){
      #match the date
      swp_select <- swp_sen_datelist[[which(names(swp_sen_datelist) == names(df_locations_method)[i])]]
      #merge two data frame
      locations_method_select[[i]] <- merge(df_locations_method[[i]], swp_select, by = "ID", sort = TRUE)
    }
  }
  else if(locations == "centers" | locations == "blocks"){
    locations_method_select <- list()
    for(i in 1:length(df_locations_method)){
      #match the date with swp.ave_sen_datelist
      swp_select <- swp.ave_sen_datelist[[which(names(swp.ave_sen_datelist) == names(df_locations_method)[i])]]
      #merge two data frame
      locations_method_select[[i]] <- merge(df_locations_method[[i]], swp_select, by = "ID", sort = TRUE)
    }
  }
  names(locations_method_select) <- names(df_locations_method)
  return(locations_method_select)
}
```

