---
title: "C1 Sentinel process"
author: "Zhehan Tang"
date: "January 17, 2018"
output: html_document
---

#package preparation
```{r}
library(dplyr)
library(raster)
library(ggplot2)
```

#read swp file
```{r}
#path_swp <- "G:/CITRIS Project/Walnut_SWP"
path_swp <- "E:/CITRIS Project/Walnut_SWP"
swp_c1_2016 <- read.csv(file.path(path_swp, "2016 C1 walnut swp.csv"), header = TRUE)
swp_c1_2017 <- read.csv(file.path(path_swp, "2017 C1 walnut swp.csv"), header = TRUE)

#change date format
swp_c1_2016$Date <- as.Date.character(swp_c1_2016$Date, format = "%d-%b-%y")
swp_c1_2017$Date <- as.Date.character(swp_c1_2017$Date, format = "%d-%b-%y")
```

#distribution of swp
```{r}
par(mfrow=c(2,1))
hist(swp_c1_2016$Avg)
hist(swp_c1_2017$Avg)
```

#Function to read sentinel file
```{r}
read_sentinel <- function(path, sentinel_image){
  #sentinel_image is the name of the sentinel file

  #get the brick
  sentinel <- brick(file.path(path, sentinel_image))
  
  #spectral subset for 10 bands
  require(raster)
  sentinel <- raster::subset(sentinel, 1:10)
  
  #rename the bands 
  names(sentinel) <- c('blue', 'green', 'red', 'rededge1', 'rededge2', 'rededge3', 'nir', 'rededge4', 'swir1', 'swir2')
  
  #output
  return(sentinel)
}
```

#Read the sentinel of match dates 
```{r}
path_wal_sen <- "E:/CITRIS Project/Walnut_sentinel"
#path_wal_sen <- "G:/CITRIS Project/Walnut_sentinel"
#path_wal_sen <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection/sentinel with match dates"

walC1_20170523_20m <- read_sentinel(path_wal_sen, "20170523_C1_20m_mean.trtif")
walC1_20170717_20m <- read_sentinel(path_wal_sen, "20170717_C1_20m_mean.tif")
walC1_20170724_20m <- read_sentinel(path_wal_sen, "20170724_C1_20m_mean.tif")

walC1_list <- list("20170523"=walC1_20170523_20m, "20170717"=walC1_20170717_20m, "20170724"=walC1_20170724_20m)

```

#Read the boundary shapefile 
```{r}
path_boundary <- "E:/CITRIS Project/site locations/Shapefiles"
#path_boundary <- "G:/CITRIS Project/site locations/Shapefiles"
#path_boundary <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection/site locations"

#shapefile of the boundary of C1
walC1_boundary <- shapefile(file.path(path_boundary, "C1_walnut_boundary.shp"))
#shapefile of the swp tree of C1
walC1_tree <- shapefile(file.path(path_boundary, "C1_walnut.shp"))

#unify the crs
walC1_boundary <- spTransform(walC1_boundary, crs(walC1_20170523_20m))
walC1_tree <- spTransform(walC1_tree, crs(walC1_20170523_20m))

#Name 
walC1_boundary$Name <- "C1_walnut_boundary"
walC1_tree$Name <- "C1_walnut_tree"

#remove extra dimension of coordinate system
walC1_tree@coords <- matrix(walC1_tree@coords[,1:2],1,2,dimnames = list(NULL,c("coords.x1","coords.x2")))

```

#Preview the image
```{r}
dev.off()
plotRGB(walC1_20170523_20m, 8,3,2, stretch = "lin")
plot(walC1_boundary, add=TRUE, border = "white")
plot(walC1_tree, add=TRUE, col = "white")

plotRGB(walC1_20170717_20m, 8,3,2, stretch = "lin")
plot(walC1_boundary, add=TRUE, border = "white")
plot(walC1_tree, add=TRUE, col = "white")

plotRGB(walC1_20170724_20m, 8,3,2, stretch = "lin")
plot(walC1_boundary, add=TRUE, border = "white")
plot(walC1_tree, add=TRUE, col = "white")
```

#The function to extract values 
```{r}
extract_sen <- function(sentinel_list, locations, method, fun){
  #sentinel_list: it is the list to store all sentinel rasterbrick
  #locations: it has 3 options: wal_blocks, wal_centers, wal_points, wal_field
  #method: it is the method used in the extract function. it has 2 optiosn: 'simple' or 'bilinear'
  #fun: it is the fun in the extract function, determining how to summarize the values. Usually it's either mean or median
  #buffer: it is the buffer in the extract function, determining the radius. Don't use when it's MAP2_blocks.  
  
  #this is the list to store all the produced data frame for each date
  n = length(sentinel_list)
  extract_sentinel_list <- vector("list", n)
  
  #In the for loop, every sublist stores a data frame extracted from the sentinel image of that date
  for(i in 1:n){
    extract_sentinel_list[[i]]<- raster::extract(x = sentinel_list[[i]], y = locations, method, fun, df = TRUE, na.rm=TRUE, buffer = NULL)
    extract_sentinel_list[[i]]$ID <- locations$Name
  }
  
  #give names (corresponding dates) to the list
  names(extract_sentinel_list) <- names(sentinel_list)
  return(extract_sentinel_list)
}


```

#Extract reflectance values of the locations
```{r}
walC1_tree_centers_sim <- extract_sen(walC1_list, walC1_tree, method = 'simple', fun = mean)

walC1_boundary_mean <- vector("list", length(walC1_list))
for (i in 1:length(walC1_boundary_mean)){
  walC1_boundary_mean[[i]] <- raster::extract(walC1_list[[i]], walC1_boundary, method = "simple", fun = mean, df = TRUE)
  walC1_boundary_mean[[i]]$ID <- walC1_boundary$Name
}
names(walC1_boundary_mean) <- names(walC1_list)
  
```

#Vegetation indices functions
```{r}
ndvi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(ndvi)
}
grvi1 <- function(sentinel){
  band_red <- sentinel$red
  band_green <- sentinel$green
  grvi1 <- (band_red - band_green)/(band_red + band_green)
  return(grvi1)
}
gndvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  gndvi <- (band_842 - band_560)/(band_842 + band_560)
  return(gndvi)
}
sr <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  sr <- band_nir/band_red
  return(sr)
}
gci <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  gci <- band_nir/band_green
}
sr.green <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  sr.green <- band_842/band_560
  return(sr.green)
}
cvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  band_665 <- sentinel$red
  cvi <- (band_842/band_560)/(band_560+band_665)
  return(cvi)
}
savi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  savi <- 1.5*(band_nir-band_red)/(band_nir+band_red+0.5)
  return(savi)
}
psri.nir <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_nir <- sentinel$nir
  psri.nir <- (band_red - band_blue)/(band_nir)
  return(psri.nir)
}
ndvi.green <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  ndvi.green <- band_green*(band_nir - band_red)/(band_nir + band_red)
  return(ndvi.green)
}
msavi2 <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  msavi2 <- (band_nir + 1) - 0.5*sqrt((2*band_nir - 1)^2 + 8*band_red)
  return(msavi2)
}
lai.savi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  lai.savi <- -log(0.371 + 1.5*(band_nir - band_red)/(band_nir + band_red + 0.5))/2.4
  return(lai.savi)
}
cri1 <- function(sentinel){
  band_green <- sentinel$green
  band_blue <- sentinel$blue
  cri1 <- (1/band_blue)-(1/band_green)
  return(cri1)
}
arvi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  arvi <- (band_nir - (2*band_red - band_blue))/(band_nir + (2*band_red-band_blue))
  return(arvi)
}
ari2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_blue <- sentinel$blue
  band_green <- sentinel$green
  ari2 <- (band_nir/band_blue)-(band_nir/band_green)
  return(ari2)
}
ndwi <- function(sentinel){
  band_swir1 <- sentinel$swir1
  band_nir <- sentinel$nir
  ndwi <- (band_nir - band_swir1)/(band_swir1 + band_nir)
  return(ndwi)
}
re.ndwi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  re.ndwi <- (band_green-band_rededge1)/(band_green+band_rededge1)
  return(re.ndwi)
}
re.ndvi.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  return(re.ndvi.1)
}
re.ndvi.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  return(re.ndvi.2)
}
re.ndvi.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  return(re.ndvi.3)
}
psri <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  psri <- (band_red - band_blue)/(band_rededge1)
  return(psri)
}
ndre.1 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_740 <- sentinel$rededge2
  ndre.1 <- (band_740-band_705)/(band_740+band_705)
  return(ndre.1)
}
ndre.2 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_783 <- sentinel$rededge3
  ndre.2 <- (band_783-band_705)/(band_783+band_705)
  return(ndre.2)
}
ndre.3 <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_783 <- sentinel$rededge3
  ndre.3 <- (band_783-band_740)/(band_783+band_740)
  return(ndre.3)
}
ndi.45 <- function(sentinel){
  band_red <- sentinel$red 
  band_rededge1 <- sentinel$rededge1
  ndi.45 <- (band_rededge1-band_red)/(band_rededge1+band_red)
  return(ndi.45)
}
mtci <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  mtci <- (band_740-band_705)/(band_705-band_665)
  return(mtci)
}
msi <- function(sentinel){
  band_swir1 <- sentinel$swir1 
  band_nir <- sentinel$nir
  msi <- band_swir1/band_nir
  return(msi)
}
mcari <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  mcari <- 1-0.2*(band_rededge1 - band_green)/(band_rededge1 - band_red)
  return(mcari)
}
ireci <- function(sentinel){
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  band_rededge2 <- sentinel$rededge2
  band_rededge1 <- sentinel$rededge1
  ireci <- (band_rededge3 - band_red)*band_rededge2/band_rededge1
  return(ireci)
}
ci.rededge <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_705 <- sentinel$rededge1
  ci.rededge <- band_783/band_705 - 1
  return(ci.rededge)
}
ci.green <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_560 <- sentinel$green
  ci.green <- band_783/band_560 - 1
  return(ci.green)
}
cri2 <- function(sentinel){
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  cri2 <- (1/band_blue) - (1/band_rededge1)
  return(cri2)
}
chl.rededge.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  chl.rededge.1 <- band_nir/band_rededge1-1
  return(chl.rededge.1)
}
chl.rededge.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  chl.rededge.2 <- band_nir/band_rededge2-1
  return(chl.rededge.2)
}
chl.rededge.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  chl.rededge.3 <- band_nir/band_rededge3-1
  return(chl.rededge.3)
}
ari1 <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  ari1 <- (1/band_green)-(1/band_rededge1)
  return(ari1)
}
tcari.osavi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  
  tcari <- 3*((band_rededge1 - band_red)-0.2*(band_rededge1 - band_green)*band_rededge1/band_red)
  osavi <- (1+0.16)*(band_nir - band_red)/(band_nir + band_red + 0.16)
}
mcari.osavi <- function(sentinel){
  
  mcari <- (sentinel$rededge1 - sentinel$red) - 0.2*(sentinel$rededge1 - sentinel$green) * sentinel$rededge1/sentinel$red
  osavi <- (1+0.16)*(sentinel$nir-sentinel$red)/(sentinel$nir+sentinel$red+0.16)
  return(mcari/osavi)
}
mcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  mcari <- ((band_740-band_705)-0.2*(band_740-band_560))*band_740/band_705
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  return(mcari/osavi)
}
tcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  tcari <- 3*((band_740 - band_705) - 0.2*(band_740 - band_560)*band_740/band_705)
  return(tcari/osavi)
}
REP <- function(sentinel){
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  band_740 <- sentinel$rededge2
  band_783 <- sentinel$rededge3
  REP <- 705 + 35*((band_665 + band_783)/2-band_705)/(band_740-band_705)
  return(REP)
}
sccci.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.1/ndvi)
}
sccci.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  band_red <- sentinel$red
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.2/ndvi)
}
sccci.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.3/ndvi)
}

```



#NDVI for the entire field overtime
```{r}
walC1_ndvi_list <- lapply(walC1_list, ndvi)

#dev.off()
par(mfrow=c(3,1))
for(i in 1:length(walC1_ndvi_list)){
  hist(raster::mask(walC1_ndvi_list[[i]],walC1_boundary), main=paste(names(walC1_ndvi_list)[i],"NDVI of the field"),xlim=c(0.9,1.0),ylim=c(0,150),xlab="")
}

par(mfrow=c(1,1))
sapply(walC1_ndvi_list, function(x) extract(x,y=walC1_boundary, fun=mean))
sapply(walC1_ndvi_list, function(x) extract(x,y=walC1_boundary, fun=median))

```

# The function to generate a data frame of reflectance and vegetation indices
```{r}
df_reflectance <- function(locations_method){

  for(i in 1:length(locations_method)){
    #change the value of reflectance (divided by 10000)
    locations_method[[i]][,-1] <- locations_method[[i]][-1]/10000
    
    #add new columns of vegetation indices
    ##ndvi
    locations_method[[i]]$ndvi <- ndvi(locations_method[[i]])
    #gci
    locations_method[[i]]$gci <- gci(locations_method[[i]])
    ##grvi1
    locations_method[[i]]$grvi1 <- grvi1(locations_method[[i]])
    ##gndvi
    locations_method[[i]]$gndvi <- gndvi(locations_method[[i]])
    ##sr
    locations_method[[i]]$sr <- sr(locations_method[[i]])
    ##sr.green
    locations_method[[i]]$sr.green <- sr.green(locations_method[[i]])
    ##cvi
    locations_method[[i]]$cvi <- cvi(locations_method[[i]])
    ##savi
    locations_method[[i]]$savi <- savi(locations_method[[i]])
    ##psri.nir
    locations_method[[i]]$psri.nir <- psri.nir(locations_method[[i]])
    ##ndvi.green
    locations_method[[i]]$ndvi.green <- ndvi.green(locations_method[[i]])
    ##msavi2
    locations_method[[i]]$msavi2 <- msavi2(locations_method[[i]])
    ##lai.savi
    locations_method[[i]]$lai.savi <- lai.savi(locations_method[[i]])
    ##cri
    locations_method[[i]]$cri1 <- cri1(locations_method[[i]])
    ##arvi
    locations_method[[i]]$arvi <- arvi(locations_method[[i]])
    ##ari2
    locations_method[[i]]$ari2 <- ari2(locations_method[[i]])
    ##ndwi
    locations_method[[i]]$ndwi <- ndwi(locations_method[[i]])
    ##re.ndwi
    locations_method[[i]]$re.ndwi <- re.ndwi(locations_method[[i]])
    ##re.ndvi.1
    locations_method[[i]]$re.ndvi.1 <- re.ndvi.1(locations_method[[i]])
    ##re.ndvi.2
    locations_method[[i]]$re.ndvi.2 <- re.ndvi.2(locations_method[[i]])
    ##re.ndvi.3
    locations_method[[i]]$re.ndvi.3 <- re.ndvi.3(locations_method[[i]])
    ##psri
    locations_method[[i]]$psri <- psri(locations_method[[i]])
    ##ndre.1
    locations_method[[i]]$ndre.1 <- ndre.1(locations_method[[i]])
    ##ndre.2
    locations_method[[i]]$ndre.2 <- ndre.2(locations_method[[i]])
    ##ndre.3
    locations_method[[i]]$ndre.3 <- ndre.3(locations_method[[i]])
    ##ndi.45
    locations_method[[i]]$ndi.45 <- ndi.45(locations_method[[i]])
    ##mtci
    locations_method[[i]]$mtci <- mtci(locations_method[[i]])
    ##msi
    locations_method[[i]]$msi <- msi(locations_method[[i]])
    ##mcari
    locations_method[[i]]$mcari <- mcari(locations_method[[i]])
    ##ireci
    locations_method[[i]]$ireci <- ireci(locations_method[[i]])
    ##ci.rededge
    locations_method[[i]]$ci.rededge <- ci.rededge(locations_method[[i]])
    ##ci.green
    locations_method[[i]]$ci.green <- ci.green(locations_method[[i]])
    ##cri2
    locations_method[[i]]$cri2 <- cri2(locations_method[[i]])
    ##chl.rededge.1
    locations_method[[i]]$chl.rededge.1 <- chl.rededge.1(locations_method[[i]])
    ##chl.rededge.2
    locations_method[[i]]$chl.rededge.2 <- chl.rededge.2(locations_method[[i]])
    ##chl.rededge.3
    locations_method[[i]]$chl.rededge.3 <- chl.rededge.3(locations_method[[i]])
    ##ari1
    locations_method[[i]]$ari1 <- ari1(locations_method[[i]])
    ##tcari.osavi
    locations_method[[i]]$tcari.osavi <- tcari.osavi(locations_method[[i]])
    ##mcari.osavi
    locations_method[[i]]$mcari.osavi <- mcari.osavi(locations_method[[i]])
    ##mcari.osavi.705
    locations_method[[i]]$mcari.osavi.705 <- mcari.osavi.705(locations_method[[i]])
    ##tcari.osavi.705
    locations_method[[i]]$tcari.osavi.705 <- tcari.osavi.705(locations_method[[i]])
    ##REP
    locations_method[[i]]$REP <- REP(locations_method[[i]])
    ##sccci.1
    locations_method[[i]]$sccci.1 <- sccci.1(locations_method[[i]])
    ##sccci.2
    locations_method[[i]]$sccci.2 <- sccci.2(locations_method[[i]])
    ##sccci.3
    locations_method[[i]]$sccci.3 <- sccci.3(locations_method[[i]])
  }
  names(locations_method) <- as.Date.character(names(locations_method), format = "%Y%m%d")
  return(locations_method)
}
```

#Use of df_reflectance function to calculate vegetation index
```{r}
df_walC1_20m <- df_reflectance(walC1_tree_centers_sim)
```

#integrate with swp data
```{r}
swp_walC1_20m <- vector("list", length(df_walC1_20m))
names(swp_walC1_20m) <- names(df_walC1_20m)
for(i in 1:length(df_walC1_20m)){
  #match the dates 
  swp_select <- swp_c1_2017[swp_c1_2017$Date == names(df_walC1_20m)[i],c(1,3,6)]
  names(swp_select)[2:3] <- c("swp","swp.bs")
  #merge two data frame
  swp_walC1_20m[[i]] <- cbind(df_walC1_20m[[i]], swp_select)
}
```

#integrate with weather data
```{r}
#read cimis weather data
path_weather <- "G:/CITRIS Project/Walnut_weather"
cimis_weather_2017 <- read.csv(file.path(path_weather, "GerberSouth_2017_temp_humid_wind.csv"), header = TRUE)
cimis_weather_2017$Date <- as.Date(cimis_weather_2017$Date)

#filter with C1 at matched dates
weather_C1_2017 <- dplyr::filter(cimis_weather_2017, Date %in% as.Date(names(swp_walC1_20m)), between(Hour, 13, 14))

#calculate daily average during the noon time 
weather_C1_2017 <- aggregate(x = weather_C1_2017[,c("temp","humid","wind")], by = list(Date = weather_C1_2017$Date), FUN = mean)

#integration
swpweather_walC1_20m <- vector("list", length(swp_walC1_20m))
names(swpweather_walC1_20m) <- names(swp_walC1_20m)
for(i in 1:length(swp_walC1_20m)){
  weather_select <- weather_C1_2017[weather_C1_2017$Date == names(swp_walC1_20m)[i],c(2,3,4)]
  swpweather_walC1_20m[[i]] <- cbind(swp_walC1_20m[[i]], weather_select) 
}

```

##VPD: vapour pressure deficit
```{r}
for(i in 1:length(swpweather_walC1_20m)){
  swpweather_walC1_20m[[i]]$vpd <- RHtoVPD(RH = swpweather_walC1_20m[[i]]$humid, TdegC = (swpweather_walC1_20m[[i]]$temp-32)*5/9)
}

```



#create a data frame and output the csv
```{r}
#combine the sublists
walC1_2017_20m <- do.call(rbind, swpweather_walC1_20m)

#output the csv
path_output <- "G:/CITRIS Project/Results"
write.csv(walC1_2017_20m, file = file.path(path_output, "walC1_2017_20m.csv"), row.names = FALSE)
```

