---
title: "Get hourly cimis station data"
author: "Zhehan Tang"
date: "February 2, 2018"
output: html_document
---

#Using Rcimis package to get data

##load the package
```{r}
library(Rcimis)
library(dplyr)
```

## Find the target station
```{r}
#Roop ranch walnut orchard
##according to the report from Allan, the Roop Ranch uses the data from Gerber South #222

#C1 walnut orchard
#cimis_C1 <- getDists(lat=39.963, lon=-122.273, n=4)

#5th avenue walnut orchard
#cimis_5th <- getDists(lat = 40.07, lon=-122.103, n=5)

```


##Request data by using CIMISweather function 
### Available dataItems: http://et.water.ca.gov/Rest/Index
Some useful dataItems
- hly-air-tmp: hourly air temperature
- hly-rel-hum: hourly relative humidity
- hly-eto: hourly CIMIS ETo
- hly-sol-rad: hourly solar radiation
- hly-vap-pres: hourly vapor pressure
- hly-net-rad: hourly net radiation
- hly-wind-spd: hourly wind speed

```{r}
cimis_May <- CIMISweather(startDate = "2017-05-01", endDate = "2017-05-31", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

cimis_June <- CIMISweather(startDate = "2017-06-01", endDate = "2017-06-30", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

cimis_July <- CIMISweather(startDate = "2017-07-01", endDate = "2017-07-31", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

cimis_Aug <- CIMISweather(startDate = "2017-08-01", endDate = "2017-08-31", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

cimis_Sept <- CIMISweather(startDate = "2017-09-01", endDate = "2017-09-30", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

cimis_Oct <- CIMISweather(startDate = "2017-10-01", endDate = "2017-10-31", targets = 222, dataItems = c("hly-air-tmp","hly-wind-spd", "hly-rel-hum"), appKey = "b6620499-260c-4f4a-af1f-14a941f9c115")

#combine them together
cimis_summer <- rbind(cimis_May, cimis_June, cimis_July, cimis_Aug, cimis_Sept, cimis_Oct)

#change the data type of the columns
cimis_summer$Date <- as.Date(cimis_summer$Date)
cimis_summer$Julian <- as.integer(cimis_summer$Julian)
cimis_summer$Hour <- as.numeric(cimis_summer$Hour)/100 #change to 1-24
#air temperature; relative humidity; wind speed
cimis_summer[,8:10] <- sapply(cimis_summer[,8:10], as.numeric)

#change the column name of the data frame 
names(cimis_summer)[8:10] <- c("temp","humid","wind")
#have a check 
str(cimis_summer)
```

##extract the dates and hours we need 
```{r}
cimis_5th_2017 <- dplyr::filter(cimis_summer, between(Hour, 12, 14), Date %in% swp_5theast_2017$Date)
cimis_C1_2017 
cimis_5th_2016 
cimis_5th_2017
cimis_roop_2017
cimis_roop_2016
cimis_roop_2017_match 

```

##calculate daily average 
```{r}
#select only the noon time
cimis_summer_noon <- dplyr::filter(cimis_summer, between(Hour, 12, 14))
#calculate daily average during the noon time 
cimis_summer_ave <- aggregate(x=cimis_summer_noon[8:10], by = list(Date = cimis_summer_noon$Date), FUN = mean)
```

It's notable that the maximum data limit is 1750 records, so you have to send multiple request and then combine multiple data frame together. 
1750/24 = 72.9. Therefore, if you want to have only one type of data, you can request for about two and half months. 

#Using API directly
Input the request directly in the browser. 
## Example of a request: 
http://et.water.ca.gov/api/data?appKey=b6620499-260c-4f4a-af1f-14a941f9c115&targets=5&startDate=2017-05-01&endDate=2017-06-01&dataItems=hly-air-tmp,%20hly-rel-hum,%20hly-eto&unitOfMeasure=M;prioritizeSCS=N 

