---
title: "PRI data analysis"
author: "Zhehan"
date: "August 24, 2017"
output: html_document
---

#Package preparation
```{r}
library(lubridate)
library(ggplot2)

```

#Read PRI_D02 data
- path_PRI: The path to store data file. 
- PRI_D02: The data frame to store PRI. 
```{r}
#path_PRI <- "E:/CITRIS Project/Pistachio_PRI"
path_PRI <- "G:/CITRIS Project/Pistachio_PRI"
#Read all PRI data
PRI_D02_1 <- read.table(file.path(path_PRI, "PRI_D02_PRIdata_2017_09_18_16_38_54.dat"), 
                      header = FALSE, 
                      sep = ",", skip = 4)[,c(1,6:9)]
PRI_D02_2 <- read.table(file.path(path_PRI, "PRI_D02_PRIdata_2017_09_18_18_00_49.dat"), 
                      header = FALSE, 
                      sep = ",", skip = 4)[,c(1,6:9)]
PRI_D02_3 <- read.table(file.path(path_PRI, "PRI_D02_PRIdata_2017_12_12_15_25_04.dat"), 
                      header = FALSE, 
                      sep = ",", skip = 4)[,c(1,5:8)]
#change column names
names(PRI_D02_1)=names(PRI_D02_2)=names(PRI_D02_3)=c("TIMESTAMP", "Down570",  "Up570", "Down531", "Up531")
PRI_D02 <- rbind(PRI_D02_1, PRI_D02_2, PRI_D02_3)



#view the data
head(PRI_D02)
#head(PRI_D02_new)
```

#Function to calculate PRI. It's more accurate to calculate it than to use the given value
- pri: the function to calculate PRI
```{r}
pri <- function(d570, u570, d531, u531){
  p570 <- d570/u570 #reflectance at 570 nm
  p531 <- d531/u531 #reflectance at 531 nm
  pri <- (p531-p570)/(p570+p531)
  return(pri)
}
```

```{r}
#Have a look at the rows with missing data
colSums(is.na(PRI_D02))
colSums(PRI_D02 == 0, na.rm = TRUE)

```

#preprocessing of PRI_D02
```{r}
PRI_D02_proc <- function(PRI_D02){

  #convert to timestamp format
  PRI_D02$TIMESTAMP <- strptime(as.character(PRI_D02$TIMESTAMP), "%Y-%m-%d %H:%M:%S")
  
  #add the column of date and time (split TIMESTAMP into two columns)
  #only the date
  PRI_D02$Date <- lubridate::date(PRI_D02$TIMESTAMP)
  #only the clock time
  PRI_D02$Time <- lubridate::hour(PRI_D02$TIMESTAMP)+minute(PRI_D02$TIMESTAMP)/60+ second(PRI_D02$TIMESTAMP)/3600
  
  #round the value to 3 digits 
  PRI_D02$Down570_round3 <- round(PRI_D02$Down570, digits = 3)
  PRI_D02$Up570_round3 <- round(PRI_D02$Up570, digits = 3)
  PRI_D02$Down531_round3 <- round(PRI_D02$Down531, digits = 3)
  PRI_D02$Up531_round3 <- round(PRI_D02$Up531, digits = 3)
  #round the value to 4 digits 
  PRI_D02$Down570_round4 <- round(PRI_D02$Down570, digits = 4)
  PRI_D02$Up570_round4 <- round(PRI_D02$Up570, digits = 4)
  PRI_D02$Down531_round4 <- round(PRI_D02$Down531, digits = 4)
  PRI_D02$Up531_round4 <- round(PRI_D02$Up531, digits = 4)


  #add the column of PRI_calc, which is the calculated PRI
  PRI_D02$PRI <- pri(d570 = PRI_D02$Down570, u570 = PRI_D02$Up570, d531 = PRI_D02$Down531, u531 = PRI_D02$Up531)
  #calculate the PRI by using the rounded 3 value
  PRI_D02$PRI_round3 <- pri(d570 = PRI_D02$Down570_round3, u570 = PRI_D02$Up570_round3, d531 = PRI_D02$Down531_round3, u531 = PRI_D02$Up531_round3)
  #calculate the PRI by using the rounded 4 value
  PRI_D02$PRI_round4 <- pri(d570 = PRI_D02$Down570_round4, u570 = PRI_D02$Up570_round4, d531 = PRI_D02$Down531_round4, u531 = PRI_D02$Up531_round4)
  
  #remove the rows with NAs
  PRI_D02 <- na.omit(PRI_D02)
  
  return(PRI_D02)
}

#run the function
PRI_D02 <- PRI_D02_proc(PRI_D02)
head(PRI_D02)
```

#(NOT useful)The function that get rid of outliers 
- PRI_D02_scale_0.5: PRI value within [-0.5, 0.5]
```{r}
PRI_scale <- function(PRI, lower, upper){
  return(PRI[PRI$PRI<upper & PRI$PRI>lower,])
}

# remove extreme PRI value that is outside of [-0.5, 0.5]
#most of PRI values are just around 0, so we can remove values outside (-0.5,0.5)
PRI_D02_scale_0.5 <- PRI_scale(PRI_D02, lower = -0.5, upper  = 0.5)
#PRI_D02_new_scale_0.5 <- PRI_scale(PRI_D02_new, lower = -0.5, upper = 0.5)
```

#date selection, remove the first day and the last day 
```{r}
##date selection function
## data is the PRI data frame, begin is the begining date, end is the end date
date_selection <- function(data, begin, end){
  data_date_selection <- data[data$Date >= begin & data$Date <= end,]
  return(data_date_selection)
}

```

# Draw the time series plot
```{r}
ggplot(PRI_D02, aes(TIMESTAMP, PRI)) + geom_line()  + ggtitle("PRI D02") +  scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week")

ggplot(PRI_D02, aes(TIMESTAMP, PRI_round3)) + geom_line()  + ggtitle("PRI D02 (round 3)") +  scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week")

ggplot(PRI_D02, aes(TIMESTAMP, PRI_round4)) + geom_line()  + ggtitle("PRI D02 (round 4)") +  scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week")


```

# Subset PRI_D02 with only noon time
```{r}
noon_selection <- function(data, early, late){
  data_noon <- data[data$Time >= early & data$Time <= late,]
  return(data_noon)
}

```


# Draw individual time series curve for different dates
```{r}

#draw individual curves for different dates


# noon time 10:00-16:00, solar noon is around 12:40 before 11-05, and it's 11:40 after 11-05
##from 10:00 to 16:00
ggplot(data = noon_selection(PRI_D02, 10, 16), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02') #+ scale_y_continuous(limits = c(-0.2,0.2))
##choose the date between 08-09 and 09-18
ggplot(data = date_selection(noon_selection(PRI_D02, 10, 16),"2017-08-09","2017-09-18"), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02 from 08.09 to 09.18') + scale_y_continuous(limits = c(-0.2,0.2))
##choose the date between 09-18 and 09-26
ggplot(data = date_selection(noon_selection(PRI_D02, 10, 16),"2017-09-18","2017-09-26"), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02 from 09.18 to 09.26') + scale_y_continuous(limits = c(-0.2,0.2))
##choose the date after 09-26
ggplot(data = date_selection(noon_selection(PRI_D02, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02 from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.2,0.2))

##from 11:00 to 15:00

#plot the rounded PRI
##choose the date after 09-26
ggplot(data = date_selection(noon_selection(PRI_D02, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI_round3, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02 (round 3) from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.2,0.2))
ggplot(data = date_selection(noon_selection(PRI_D02, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI_round4, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D02 (round 4) from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.2,0.2))


```



# Calculate daily average, using only the data during noon time
##Function to calculate daily average using only the noon time
```{r}
### calculate daily average
PRI_daily_ave <- function(data, early, late){
  ### split by different date
  PRI_D02_noon_split <- split(noon_selection(data, early, late), noon_selection(data, early, late)$Date)
  # need to change the number of columns in it. 14 is the column number of PRI_calc
  PRI_D02_daily <- lapply(lapply(PRI_D02_noon_split, '[[', 13 ), mean)
  ### convert it to a data frame 
  PRI_D02_daily <- data.frame("date" = ymd(names(PRI_D02_daily)), "PRI" = unlist(PRI_D02_daily))
  
  return(PRI_D02_daily)
}

##Another way to calculate the daily average
PRI_daily_ave_2 <- function(data, early, late, begin, end){
  #select only the noon time and only the date that I'm interested in 
  PRI_date <- date_selection(data, begin, end)
  PRI_date_noon <- noon_selection(PRI_date, early, late)
  
  #aggregate
  PRI_date_noon <- aggregate(x = PRI_date_noon[,-c(1,6,7)], by = list(Date = PRI_date_noon$Date), FUN = mean) #c(1,6,7) is the time variables
  
  return(PRI_date_noon)
}


```


```{r}

# Draw a plot of 10:00 - 16
##from 08-09 to 11-15
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 10:00-16:00 from 08-09 to 11-15') +  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 3) 10:00-16:00 from 08-09 to 11-15')+  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 4) 10:00-16:00 from 08-09 to 11-15')+  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")

##from 09-26 to 11-15
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 10:00-16:00 from 09-26 to 11-15')
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 3) 10:00-16:00 from 09-26 to 11-15')
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 4) 10:00-16:00 from 09-26 to 11-15')


##from 08-09 to 09-18 (Three are the same)
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 10:00-16:00 from 08-09 to 09-18')
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 3) 10:00-16:00 from 08-09 to 09-18')
ggplot(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D02 (round 4) 10:00-16:00 from 08-09 to 09-18')


```

# Read D04 Data
```{r}
PRI_D04 <- read.csv(file.path(path_PRI, "FLO_D04_Pistachio_PRIdata_12Dec2017.csv"), header = FALSE, na.strings = "***", skip = 3)[,c(1,7,8)]  # Replace * with NAs
colnames(PRI_D04) <- c("TIMESTAMP","Down531","Down570")

#view the data
head(PRI_D04)
```

# Preprocessing of PRI_D04
```{r}
PRI_D04_proc <- function(PRI_D04){
  # %p is the AM/PM indicator, and it should be used in conjunction with %I and not with %h
  PRI_D04$TIMESTAMP <- strptime(as.character(PRI_D04$TIMESTAMP), "%m/%d/%Y %I:%M:%S %p" )
  #only after 2017-08-08, as we install the sensor in 2017-08-09
  PRI_D04 <- PRI_D04[date(PRI_D04$TIMESTAMP)>"2017-08-08",]
  
  #subset PRI_D04, only remain the records that have the same time as D02
  PRI_D04 <- PRI_D04[match(PRI_D02$TIMESTAMP, PRI_D04$TIMESTAMP, nomatch = 0),]
  PRI_D02_match <- PRI_D02[match(PRI_D04$TIMESTAMP, PRI_D02$TIMESTAMP, nomatch = 0),]
  
  #add another two columns to PRI_D04 (Up531 and Up570)
  PRI_D04$Up531 <- PRI_D02_match$Up531
  PRI_D04$Up570 <- PRI_D02_match$Up570
  
  #add the column of date and time (split TIMESTAMP into two columns)
  #only the date
  PRI_D04$Date <- date(PRI_D04$TIMESTAMP)
  #only the clock time
  PRI_D04$Time <- hour(PRI_D04$TIMESTAMP)+minute(PRI_D04$TIMESTAMP)/60+ second(PRI_D04$TIMESTAMP)/3600
  
  #round the value to 3 digits 
  PRI_D04$Down570_round3 <- round(PRI_D04$Down570, digits = 3)
  PRI_D04$Up570_round3 <- round(PRI_D04$Up570, digits = 3)
  PRI_D04$Down531_round3 <- round(PRI_D04$Down531, digits = 3)
  PRI_D04$Up531_round3 <- round(PRI_D04$Up531, digits = 3)
  #round the value to 4 digits 
  PRI_D04$Down570_round4 <- round(PRI_D04$Down570, digits = 4)
  PRI_D04$Up570_round4 <- round(PRI_D04$Up570, digits = 4)
  PRI_D04$Down531_round4 <- round(PRI_D04$Down531, digits = 4)
  PRI_D04$Up531_round4 <- round(PRI_D04$Up531, digits = 4)
  
  #Calculate PRI for D04
  PRI_D04$PRI <- pri(d570 = PRI_D04$Down570, u570 = PRI_D04$Up570, d531 = PRI_D04$Down531, u531 = PRI_D04$Up531)
  #calculate the PRI by using the rounded 3 value
  PRI_D04$PRI_round3 <- pri(d570 = PRI_D04$Down570_round3, u570 = PRI_D04$Up570_round3, d531 = PRI_D04$Down531_round3, u531 = PRI_D04$Up531_round3)
  #calculate the PRI by using the rounded 4 value
  PRI_D04$PRI_round4 <- pri(d570 = PRI_D04$Down570_round4, u570 = PRI_D04$Up570_round4, d531 = PRI_D04$Down531_round4, u531 = PRI_D04$Up531_round4)
  
  #remove the rows with NAs
  PRI_D04 <- na.omit(PRI_D04)
  
  #Reorder the columns 
  PRI_D04 <- PRI_D04[,names(PRI_D02)]
  
  return(PRI_D04)
}

PRI_D04 <- PRI_D04_proc(PRI_D04)
head(PRI_D04)
```

# get an overview of the PRI_D04
```{r}
str(PRI_D04)
summary(PRI_D04$PRI)
hist(PRI_D04$PRI)
```

# Draw the time series plots for PRI_D04
```{r}
# the first plot uses the smallest time unit (30 minutes)
ggplot(PRI_D04, aes(TIMESTAMP, PRI)) + geom_line() + scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week") + ggtitle("PRI D04") + scale_y_continuous(limits = c(-0.5,0.5))

ggplot(PRI_D04, aes(TIMESTAMP, PRI_round3)) + geom_line() + scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week") + ggtitle("PRI D04 (round 3)")+ scale_y_continuous(limits = c(-0.5,0.5))

ggplot(PRI_D04, aes(TIMESTAMP, PRI_round4)) + geom_line() + scale_x_datetime("Time", date_labels = "%m-%d", date_breaks = "1 week") + ggtitle("PRI D04 (round 4)") + scale_y_continuous(limits = c(-0.5,0.5))

```

# Draw individual time series curve for different dates for PRI_D04
```{r}

#draw individual curves for different dates

#The plot that select only noon time
#connecting line
#solar noon is around 13:00
ggplot(data = noon_selection(PRI_D04, 10, 16), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04')
##choose the date between 08-09 and 09-18
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-08-09","2017-09-18"), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 from 08.09 to 09.18') + scale_y_continuous(limits = c(-0.1,0.2))
##choose the date after 09-26
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.1,0.2))

#plot the rounded PRI
##choose the date between 08-09 to 09-18
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-08-09","2017-09-18"), aes(x = Time, y = PRI_round3, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 (round 3) from 08.09 to 09.18') + scale_y_continuous(limits = c(-0.1,0.2))
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-08-09","2017-09-18"), aes(x = Time, y = PRI_round4, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 (round 4) from 08.09 to 09.18') + scale_y_continuous(limits = c(-0.1,0.2))

##choose the date after 09-26
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI_round3, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 (round 3) from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.2,0.2))
ggplot(data = date_selection(noon_selection(PRI_D04, 10, 16),"2017-09-26","2017-11-15"), aes(x = Time, y = PRI_round4, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle('10:00-16:00 curve of PRI_D04 (round 4) from 09.26 to 11.15') + scale_y_continuous(limits = c(-0.2,0.2))





```

#The function to calculate steady state PRI and delta PRI
```{r}
#delta.pri <- function(pri, hour){
#  steady.pri <- pri[pri$Time == hour,]
#  delta.pri <- rep(0, nrow(pri))
#  for(i in 1:nrow(pri)){
#    for(j in 1:nrow(steady.pri)){
#      if (pri[i,]$Date == steady.pri[j,]$Date){
#        delta.pri[i] <- pri[i,]$PRI - steady.pri[j,]$PRI
#      }
#    }
#  }
#  return(delta.pri)
#}

#PRI_D04$PRI_delta <- NULL 
#PRI_D04$PRI_delta <- delta.pri(PRI_D04, 9)
#PRI_D02$PRI_delta <- delta.pri(PRI_D02, 9)
```

```{r}
##plot of delta pri
#ggplot(data = noon_selection(PRI_D04, 10, 16), aes(x = Time, y = PRI_delta, group = Date)) + geom_point(aes(colour = as.factor(Date))) + geom_line(aes(colour = as.factor(Date))) + ggtitle('10:00-16:30 curve of delta PRI_D04')

#ggplot(data = noon_selection(PRI_D02, 10, 16), aes(x = Time, y = PRI_delta, group = Date)) + geom_point(aes(colour = as.factor(Date))) + geom_line(aes(colour = as.factor(Date))) + ggtitle('10:00-16:30 curve of delta PRI_D02')

```




#Calculate daily average, using only the data during noon time and compare with PRI_D02
##function to 
```{r}
### calculate daily average
PRI_daily_ave_D04 <- function(data, early, late){
  ### split by different date
  PRI_D04_noon_split <- split(noon_selection(data, early, late), noon_selection(data, early, late)$Date)
  # need to change the number of columns in it. 6 is the column number of PRI_calc
  PRI_D04_daily <- lapply(lapply(PRI_D04_noon_split, '[[', 6 ), mean)
  ### convert it to a data frame 
  PRI_D04_daily <- data.frame("date" = ymd(names(PRI_D04_daily)), "PRI" = unlist(PRI_D04_daily))
  
  return(PRI_D04_daily)
}

##Another way to calculate the daily average
PRI_daily_ave_2 <- function(data, early, late, begin, end){
  #select only the noon time and only the date that I'm interested in 
  PRI_date <- date_selection(data, begin, end)
  PRI_date_noon <- noon_selection(PRI_date, early, late)
  
  #aggregate
  PRI_date_noon <- aggregate(x = PRI_date_noon[,-c(1,6,7)], by = list(Date = PRI_date_noon$Date), FUN = mean) #c(1,6,7) is the time variables
  
  return(PRI_date_noon)
}



```

```{r}
# Draw a plot of 10:00 - 16
##from 08-09 to 11-15
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 10:00-16:00 from 08-09 to 11-15') +  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 3) 10:00-16:00 from 08-09 to 11-15')+  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-11-15"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 4) 10:00-16:00 from 08-09 to 11-15')+  scale_x_date(date_labels = "%m-%d", date_breaks = "2 weeks")

##from 09-26 to 11-15
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 10:00-16:00 from 09-26 to 11-15')
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 3) 10:00-16:00 from 09-26 to 11-15')
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-09-26", "2017-11-15"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 4) 10:00-16:00 from 09-26 to 11-15')


##from 08-09 to 09-18 
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 10:00-16:00 from 08-09 to 09-18')
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI_round3)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 3) 10:00-16:00 from 08-09 to 09-18')
ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-09-18"), aes(x = Date, y = PRI_round4)) + geom_point() + geom_line() + ggtitle('Daily Average PRI D04 (round 4) 10:00-16:00 from 08-09 to 09-18')


```

#compare D02 with D04
```{r}
#compare D02 and D04
# Draw a plot of 11:00 - 15:00

#ggplot(data = PRI_daily_ave_2(PRI_D04, 10, 16, "2017-08-09", "2017-11-15"), aes(x = date, y = PRI)) + geom_point() + geom_line() + ggtitle('Daily Average PRI 10:00-16:00 (Red is D02 and Black is D04)') + geom_line(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-11-15"), aes(x = date, y = PRI), color = "red") + geom_point(data = PRI_daily_ave_2(PRI_D02, 10, 16, "2017-08-09", "2017-11-15"), aes(x = date, y = PRI), color = "red") + scale_colour_manual("", breaks = c("D02","D04"), values = c("D02"="red", "D04"="black"))

```


### The daily average seems to be a good indicator of water potential
- The daily average of D04 is higher than D02, and the water potential for D04 is higher than D02. According to the SWP measuremennt by Giulia on Sept 19th, the SWP D02 is -12.6, the SWP D04 is -10. 


### Check the diurnal cycle of incoming radiation
- Very clear diurnal cycle, peak at 13:00. 
```{r}
#uP531 from D04
ggplot(data = PRI_D04, aes(x = Time, y = Up531, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up531")
ggplot(data = date_selection(PRI_D04, "2017-08-09", "2017-09-18"), aes(x = Time, y = Up531, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up531")
ggplot(data = date_selection(PRI_D04, "2017-09-26", "2017-11-15"), aes(x = Time, y = Up531, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up531")

#Up570 from D04
ggplot(data = PRI_D04, aes(x = Time, y = Up570, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up570")
ggplot(data = date_selection(PRI_D04, "2017-08-09", "2017-09-18"), aes(x = Time, y = Up570, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up570")
ggplot(data = date_selection(PRI_D04, "2017-09-30", "2017-11-15"), aes(x = Time, y = Up570, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up570 after 09-30") + scale_x_time(limits = c(0,24))



ggplot(data = PRI_D02, aes(x = Time, y = Up531, color = as.factor(Date))) + geom_point() + geom_line() + ggtitle("Incoming radiation up531")
ggplot(data = date_selection(PRI_D02, "2017-08-09", "2017-09-18"), aes(x=Time, y=Up531,color = as.factor(Date)))+geom_point()+geom_line()
ggplot(data = date_selection(PRI_D02, "2017-09-26", "2017-11-15"), aes(x=Time, y=Up531,color = as.factor(Date)))+geom_point()+geom_line()



ggplot(data = PRI_D04, aes(x = Time, y = Up570, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Incoming radiation up570")


### Check the diurnal cycle of upcoming radiation
# for PRI_D04
ggplot(data = PRI_D04, aes(x = Time, y = Down531, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Radiation Down531 for D04")

ggplot(data = PRI_D04, aes(x = Time, y = Down570, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Radiation Down570 for D04")

# for PRI_D02
ggplot(data = PRI_D02, aes(x = Time, y = Down531, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Radiation Down531 for D02")

ggplot(data = PRI_D02, aes(x = Time, y = Down570, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Radiation Down570 for D02")

```

### zoom in the plot of down radiation of PRI_D02 to see why there are only some points
```{r}
ggplot(data = noon_selection(PRI_D02, 11, 12), aes(x = Time, y = Down531, group = Date)) + geom_point(aes(color = as.factor(Date))) + geom_line(aes(color = as.factor(Date))) + ggtitle("Radiation Down531 for D02 11:00-12:00")
PRI_D02$Time
ddply(noon_selection(PRI_D02, 10, 16), .(Time), function(x) unique(x$PRI_calc))
ddply(date_selection(PRI_D02, "2017-09-01","2017-09-05"), .(Time), function(x) unique(x$PRI_calc))
unique(noon_selection(PRI_D02, 11, 12)$Down531)

```

### check the distribution of down sensors
```{r}
par(mfrow = c(2,2))
hist(PRI_D02$Down531, breaks = seq(0, 0.030, 0.0001), ylim = c(0,80))
hist(PRI_D04$Down531, breaks = seq(0, 0.030, 0.0001), ylim = c(0,80))
hist(PRI_D02$Down570, breaks = seq(0, 0.030, 0.0001), ylim = c(0,80))
hist(PRI_D04$Down570, breaks = seq(0, 0.030, 0.0001), ylim = c(0,80))

```

#draw multiple curves with 2 y-axis 
```{r}
PRI_ave_D02 <- PRI_daily_ave_2(PRI_D02, 11, 15, "2017-08-09", "2017-11-15")
PRI_ave_D04 <- PRI_daily_ave_2(PRI_D04, 11, 15, "2017-08-09", "2017-11-15")


par(mfrow =  c(1,1), mar =  c(5,5,2,5))
plot(y = PRI_ave_D04$PRI, x = PRI_ave_D04$Date, type = 'l', col = "blue", ylab = "PRI values", xlab = "Date", ylim = c(0.012, -0.11))
lines(y = PRI_ave_D02$PRI, x = PRI_ave_D02$Date, col = "red")
par(new = T)
with(dplyr::filter(swp_pis_center, date > as.Date("2017-08-08")), plot(x = date, y = SWP.Bar, pch = 16, axes = F, xlab = NA, ylab = NA, col = as.factor(station)))
axis(side=4)
mtext(side = 4, line = 3, 'SWP (Bars)')
legend('topleft', legend = c("D02 SWP", "D04 SWP", "D02 PRI", "D04 PRI"), lty = c(0,0,1,1), pch = c(16, 16, NA, NA), col = c("red", "blue", "red", "blue"), cex = 0.5)


a <- merge(swp_pis_center[swp_pis_center$station=="FLO_D02",], PRI_ave_D02, by.x = "date", by.y = "Date")
b <- merge(swp_pis_center[swp_pis_center$station=="FLO_D04",], PRI_ave_D04, by.x = "date", by.y = "Date")
d <- rbind(a,b)
summary(lm(d$SWP.Bar~d$PRI))
plot(d$SWP.Bar, d$PRI)
ggplot(data = d, aes(x = PRI, y = SWP.Bar))+geom_point(aes(color = station))+geom_smooth(method = 'lm')

#block average
par(mfrow =  c(1,1), mar =  c(5,5,2,5))
plot(y = PRI_ave_D04$PRI, x = PRI_ave_D04$Date, type = 'l', col = "blue", ylab = "PRI values", xlab = "Date", ylim = c(-0.012, 0.10))
lines(y = PRI_ave_D02$PRI, x = PRI_ave_D02$Date, col = "red")
par(new = T)
with(dplyr::filter(swp_pis_ave, date > as.Date("2017-08-08")), plot(x = date, y = swp, pch = 16, axes = F, xlab = NA, ylab = NA, col = as.factor(station)))
axis(side=4)
mtext(side = 4, line = 3, 'SWP (Bars)')
legend('topleft', legend = c("D02 SWP", "D04 SWP", "D02 PRI", "D04 PRI"), lty = c(0,0,1,1), pch = c(16, 16, NA, NA), col = c("red", "blue", "red", "blue"), cex = 0.5)
```

