---
title: "sentinel 20m process with match dates"
author: "Zhehan Tang"
date: "January 29, 2018"
output: html_document
---

#Package preparation
```{r}
library(sp)
library(raster)
library(ggplot2)
library(dplyr)
library(plyr)
library(rgeos)
library(rgdal)
library(hsdar)
```


# Read and process swp data
##Read updated swp data csv
swp: the dataframe to store raw swp data
```{r}
path_swp <- "G:/CITRIS Project/Walnut_SWP"
#path_swp <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection"
swp <- read.csv(file.path(path_swp, "2017 Roop walnut swp.csv"), header = TRUE)
#SELECT columns
swp <- dplyr::select(swp, Measure.ment.Date, Rep, Irrigation.Treatment.Code, Tree.., Orchard.SWP........bars.,Bars.Below.Base.Line)
#change the colname of the dataframe
colnames(swp) <- c("date", "rep", "irrigation", "tree", "swp", "swp.bs")
#change the date format
swp$date <- as.Date(swp$date, format = "%m/%d/%Y")

#change the name of irrigation 
swp$irrigation <- gsub(swp$irrigation, pattern = " ", replacement = "_")
swp$irrigation <- gsub(swp$irrigation, pattern = "Grower_Practice", replacement = "0_bar_below")

#add a new column of indiviudal tree
swp$ID <- paste(swp$irrigation,"Rep", swp$rep, "Tree", swp$tree, sep = "_")

#change the class of each column
swp$rep <- as.factor(swp$rep)
swp$irrigation <- as.factor(swp$irrigation)
swp$tree <- as.factor(swp$tree)
swp$ID <- as.factor(swp$ID)
#change the order of the data frame, making ID at the beginging
swp <- swp %>% dplyr::select(ID, everything())

head(swp)
tail(swp)

swp_ID_list <- split(swp, swp$ID)
```

##Select the match dates
swp_sen: the data frame that stores the swp of the dates that match sentinel dates
swp_sen_datelist: split swp_sen into a list based on dates
```{r}
swp_sen <- subset(swp,date %in% as.Date(c('2017-06-19', '2017-07-17','2017-07-24','2017-08-18','2017-09-22'))) 
dim(swp_sen)
#split with dates
swp_sen_datelist <- split(swp_sen, swp_sen$date)
```

##Calculate block average for swp_sentinel
swp.ave_sen_datelist: block average swp split into a list based on dates 
```{r}
#create an empty list to swp_ave
swp.ave_sen_datelist <- list()
for(i in 1:length(swp_sen_datelist)){
  #aggregate to calculate the average of swp from two trees in th same block
  swp.ave_sen_datelist[[i]] <- aggregate(x=swp_sen_datelist[[i]][6:7], by = list(date = swp_sen_datelist[[i]]$date, rep=swp_sen_datelist[[i]]$rep, irrigation = swp_sen_datelist[[i]]$irrigation), FUN = mean)
  #rename the fourth column from "x" to "swp"
  colnames(swp.ave_sen_datelist[[i]])[4] = "swp"
  #create a new column called "ID", which is the block name 
  swp.ave_sen_datelist[[i]]$ID <- paste(swp.ave_sen_datelist[[i]]$irrigation, "Rep", swp.ave_sen_datelist[[i]]$rep, sep = "_")
  #change the ID column from character to factor
  swp.ave_sen_datelist[[i]]$ID <- as.factor(swp.ave_sen_datelist[[i]]$ID)
  #make the ID column come to the front 
  #swp.ave_sen_datelist[[i]] <- swp.ave_sen_datelist[[i]] %>% dplyr::select(ID, everything())

  #name each sublist
  names(swp.ave_sen_datelist)[i] <- names(swp_sen_datelist)[i]

}

```

#Function to read sentinel file
```{r}
read_sentinel <- function(path, sentinel_image){
  #sentinel_image is the name of the sentinel file

  #get the brick
  sentinel <- brick(file.path(path, sentinel_image))
  
  #spectral subset for 10 bands
  require(raster)
  sentinel <- raster::subset(sentinel, 1:10)
  
  #rename the bands 
  names(sentinel) <- c('blue', 'green', 'red', 'rededge1', 'rededge2', 'rededge3', 'nir', 'rededge4', 'swir1', 'swir2')
  
  #output
  return(sentinel)
}
```

#Read the sentinel of match dates 
```{r}
path_wal_sen <- "G:/CITRIS Project/Walnut_sentinel"
#path_wal_sen <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection/sentinel with match dates"

roop_20170619_20m <- read_sentinel(path_wal_sen, "20170619_Roop_20m_mean.tif")
roop_20170717_20m <- read_sentinel(path_wal_sen, "20170717_Roop_20m_mean.tif")
roop_20170724_20m <- read_sentinel(path_wal_sen, "20170724_Roop_20m_mean.tif")
roop_20170818_20m <- read_sentinel(path_wal_sen, "20170818_Roop_20m_mean.tif")
roop_20170922_20m <- read_sentinel(path_wal_sen, "20170922_Roop_20m_mean.tif")

#wal_sen_20170503 <- read_sentinel(path_wal_sen, "wal_sen_20170503_10m.tif")
#wal_sen_20170813 <- read_sentinel(path_wal_sen, "wal_sen_20170813_10m.tif")

roop_list <- list("20170619"=roop_20170619_20m,"20170717"=roop_20170717_20m,"20170724"=roop_20170724_20m,"20170818"=roop_20170818_20m, "20170922"=roop_20170922_20m)
```

#Read the boundary shapefile
wal_field: the big boundary of the whole field
wal_block: the boundary of each block
wal_centers:
```{r}
path_boundary <- "G:/CITRIS Project/site locations/Shapefiles"
#path_boundary <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection/site locations"

#this is the shapefile of the boundary of blocks
wal_blocks <- shapefile(file.path(path_boundary, "MAP2_blocks.shp"))
#use '_' to replace ' ' and ','
wal_blocks$Name <- gsub(x=gsub(x = wal_blocks$Name, replacement = '', pattern = ","),replacement ="_", pattern = " " )
#change grower's practice to 0_bar_below
wal_blocks$Name <- gsub(wal_blocks$Name, pattern = "Grower's_practice", replacement = "0_bar_below")

#unify the crs
wal_blocks <- spTransform(wal_blocks, crs(roop_20170717_20m))

#remove the big boundary
wal_field <- wal_blocks[wal_blocks$Name == "2014_Tehama_Walnut_Irrigation_Treatment",]
wal_blocks <- wal_blocks[wal_blocks$Name != "2014_Tehama_Walnut_Irrigation_Treatment",]


#----------------------------------------------------#

#this is the shapefile of the poitns 
wal_points <- shapefile(file.path(path_boundary, "MAP2_points.shp"))
#use '_' to replace ' ' and ','
wal_points$Name <- gsub(x=gsub(x = wal_points$Name, replacement = '', pattern = ","),replacement ="_", pattern = " " )
#change grower's practice to 0_bar_below
wal_points$Name <- gsub(wal_points$Name, pattern = "Grower's_practice", replacement = "0_bar_below")
#change "3_bar" to "3_bars"
wal_points$Name <- gsub(wal_points$Name, pattern = "3_bar_", replacement = "3_bars_")
#change "4_bar" to "4_bars"
wal_points$Name <- gsub(wal_points$Name, pattern = "4_bar_", replacement = "4_bars_")
#remove extra dimension of coordinate system
wal_points@coords <- wal_points@coords[,1:2]
#unify the crs
wal_points <- spTransform(wal_points, crs(roop_20170717_20m))

#-------------------------------------------------------#
#Add a column of blocks to wal_points
wal_points$blocks <- sapply(strsplit(wal_points$Name, "_Tree",1),'[',1)
#split them by blocks so that we can have 
wal_centers_split <- split(wal_points, wal_points$blocks)
wal_centers_split <- lapply(wal_centers_split, function(x) SpatialPointsDataFrame(coords = matrix(colMeans(x@coords),1,2), proj4string = x@proj4string, data = data.frame(Name = unique(x$blocks))))

wal_centers <- do.call(rbind,wal_centers_split)
wal_centers$Name <- as.character(wal_centers$Name)

#-------------------------------------------------------#
#order it
wal_blocks <- wal_blocks[order(wal_blocks$Name),]
wal_centers <- wal_centers[order(wal_centers$Name),]
wal_points <- wal_points[order(wal_points$Name),]

#-------------------------------------------------------#
#plot it
#plot(wal_field)
#plot(wal_blocks, add = TRUE )
#plot(wal_centers, add= TRUE, pch = 20, col = 'red')
#plot(wal_points, add = TRUE)

#plot(wal_field)
#plot(wal_blocks, add = TRUE)
#plot(wal_blocks[wal_blocks$Name=="4_bars_below_Rep_5",], add = TRUE, #col='red')
#plot(wal_blocks[wal_blocks$Name=="4_bars_below_Rep_4",], add = TRUE, col='red')
```

#Preview the image
```{r}
plotRGB(roop_20170818_20m, 3, 2, 1, stretch="hist")
plot(wal_field, add=TRUE)
plot(wal_points, col="white",add=TRUE)
plot(wal_centers, col="red", add=TRUE, pch=20)
plot(wal_blocks, add=TRUE, alpha=0.1, border="white")

plotRGB(roop_20170818_20m, 3, 2, 1, stretch="lin")
plot(wal_field, add=TRUE)
plot(wal_points, col="white",add=TRUE)
plot(wal_centers, col="red", add=TRUE, pch=20)
plot(wal_blocks, add=TRUE, alpha=0.1, border="white")
```

# The function to extract values of the centers and their 10m buffer
- Also test two different extract methods: simple and bilinear. If 'simple' values for the cell a point falls in are returned. If 'bilinear' the returned values are interpolated from the values of the four nearest raster cells.
```{r}
extract_sen <- function(sentinel_list, locations, method, fun){
  #sentinel_list: it is the list to store all sentinel rasterbrick
  #locations: it has 3 options: wal_blocks, wal_centers, wal_points, wal_field
  #method: it is the method used in the extract function. it has 2 optiosn: 'simple' or 'bilinear'
  #fun: it is the fun in the extract function, determining how to summarize the values. Usually it's either mean or median
  #buffer: it is the buffer in the extract function, determining the radius. Don't use when it's MAP2_blocks.  
  
  #this is the list to store all the produced data frame for each date
  extract_sentinel_list <- list()
  
  #In the for loop, every sublist stores a data frame extracted from the sentinel image of that date
  for(i in 1:length(sentinel_list)){
    extract_sentinel_list[[i]]<- raster::extract(x = sentinel_list[[i]], y = locations, method, fun, df = TRUE, na.rm=TRUE, buffer = NULL)
    extract_sentinel_list[[i]]$ID <- locations$Name
  }
  
  #give names (corresponding dates) to the list
  names(extract_sentinel_list) <- names(sentinel_list)
  return(extract_sentinel_list)
}

```

#Extract reflectance values of the locations
```{r}
roop_centers_sim <- extract_sen(roop_list, wal_centers, method = 'simple', fun = mean)
#roop_points_sim <-  extract_sen(roop_list, wal_points, method = 'simple', fun = mean)


#WalSen_blocks_sim <- extract_sen(wal_sen_list, wal_blocks, method='simple', fun=mean)
#WalSen_blocks_bil <- extract_sen(wal_sen_list, wal_blocks, method='bilinear', fun=mean)

```

#Vegetation indices functions
```{r}
ndvi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(ndvi)
}
grvi1 <- function(sentinel){
  band_red <- sentinel$red
  band_green <- sentinel$green
  grvi1 <- (band_red - band_green)/(band_red + band_green)
  return(grvi1)
}
gndvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  gndvi <- (band_842 - band_560)/(band_842 + band_560)
  return(gndvi)
}
sr <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  sr <- band_nir/band_red
  return(sr)
}
gci <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  gci <- band_nir/band_green
}
sr.green <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  sr.green <- band_842/band_560
  return(sr.green)
}
cvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  band_665 <- sentinel$red
  cvi <- (band_842/band_560)/(band_560+band_665)
  return(cvi)
}
savi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  savi <- 1.5*(band_nir-band_red)/(band_nir+band_red+0.5)
  return(savi)
}
psri.nir <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_nir <- sentinel$nir
  psri.nir <- (band_red - band_blue)/(band_nir)
  return(psri.nir)
}
ndvi.green <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  ndvi.green <- band_green*(band_nir - band_red)/(band_nir + band_red)
  return(ndvi.green)
}
msavi2 <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  msavi2 <- (band_nir + 1) - 0.5*sqrt((2*band_nir - 1)^2 + 8*band_red)
  return(msavi2)
}
lai.savi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  lai.savi <- -log(0.371 + 1.5*(band_nir - band_red)/(band_nir + band_red + 0.5))/2.4
  return(lai.savi)
}
cri1 <- function(sentinel){
  band_green <- sentinel$green
  band_blue <- sentinel$blue
  cri1 <- (1/band_blue)-(1/band_green)
  return(cri1)
}
arvi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  arvi <- (band_nir - (2*band_red - band_blue))/(band_nir + (2*band_red-band_blue))
  return(arvi)
}
ari2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_blue <- sentinel$blue
  band_green <- sentinel$green
  ari2 <- (band_nir/band_blue)-(band_nir/band_green)
  return(ari2)
}
ndwi <- function(sentinel){
  band_swir1 <- sentinel$swir1
  band_nir <- sentinel$nir
  ndwi <- (band_nir - band_swir1)/(band_swir1 + band_nir)
  return(ndwi)
}
re.ndwi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  re.ndwi <- (band_green-band_rededge1)/(band_green+band_rededge1)
  return(re.ndwi)
}
re.ndvi.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  return(re.ndvi.1)
}
re.ndvi.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  return(re.ndvi.2)
}
re.ndvi.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  return(re.ndvi.3)
}
psri <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  psri <- (band_red - band_blue)/(band_rededge1)
  return(psri)
}
ndre.1 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_740 <- sentinel$rededge2
  ndre.1 <- (band_740-band_705)/(band_740+band_705)
  return(ndre.1)
}
ndre.2 <- function(sentinel){
  band_705 <- sentinel$rededge1 
  band_783 <- sentinel$rededge3
  ndre.2 <- (band_783-band_705)/(band_783+band_705)
  return(ndre.2)
}
ndre.3 <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_783 <- sentinel$rededge3
  ndre.3 <- (band_783-band_740)/(band_783+band_740)
  return(ndre.3)
}
ndi.45 <- function(sentinel){
  band_red <- sentinel$red 
  band_rededge1 <- sentinel$rededge1
  ndi.45 <- (band_rededge1-band_red)/(band_rededge1+band_red)
  return(ndi.45)
}
mtci <- function(sentinel){
  band_740 <- sentinel$rededge2 
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  mtci <- (band_740-band_705)/(band_705-band_665)
  return(mtci)
}
msi <- function(sentinel){
  band_swir1 <- sentinel$swir1 
  band_nir <- sentinel$nir
  msi <- band_swir1/band_nir
  return(msi)
}
mcari <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  mcari <- 1-0.2*(band_rededge1 - band_green)/(band_rededge1 - band_red)
  return(mcari)
}
ireci <- function(sentinel){
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  band_rededge2 <- sentinel$rededge2
  band_rededge1 <- sentinel$rededge1
  ireci <- (band_rededge3 - band_red)*band_rededge2/band_rededge1
  return(ireci)
}
ci.rededge <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_705 <- sentinel$rededge1
  ci.rededge <- band_783/band_705 - 1
  return(ci.rededge)
}
ci.green <- function(sentinel){
  band_783 <- sentinel$rededge3
  band_560 <- sentinel$green
  ci.green <- band_783/band_560 - 1
  return(ci.green)
}
cri2 <- function(sentinel){
  band_blue <- sentinel$blue
  band_rededge1 <- sentinel$rededge1
  cri2 <- (1/band_blue) - (1/band_rededge1)
  return(cri2)
}
chl.rededge.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  chl.rededge.1 <- band_nir/band_rededge1-1
  return(chl.rededge.1)
}
chl.rededge.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  chl.rededge.2 <- band_nir/band_rededge2-1
  return(chl.rededge.2)
}
chl.rededge.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  chl.rededge.3 <- band_nir/band_rededge3-1
  return(chl.rededge.3)
}
ari1 <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_green <- sentinel$green
  ari1 <- (1/band_green)-(1/band_rededge1)
  return(ari1)
}
tcari.osavi <- function(sentinel){
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  
  tcari <- 3*((band_rededge1 - band_red)-0.2*(band_rededge1 - band_green)*band_rededge1/band_red)
  osavi <- (1+0.16)*(band_nir - band_red)/(band_nir + band_red + 0.16)
}
mcari.osavi <- function(sentinel){
  
  mcari <- (sentinel$rededge1 - sentinel$red) - 0.2*(sentinel$rededge1 - sentinel$green) * sentinel$rededge1/sentinel$red
  osavi <- (1+0.16)*(sentinel$nir-sentinel$red)/(sentinel$nir+sentinel$red+0.16)
  return(mcari/osavi)
}
mcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  mcari <- ((band_740-band_705)-0.2*(band_740-band_560))*band_740/band_705
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  return(mcari/osavi)
}
tcari.osavi.705 <- function(sentinel){
  band_740 <- sentinel$rededge2
  band_705 <- sentinel$rededge1
  band_560 <- sentinel$green
  osavi <- (1+0.16)*(band_740-band_705)/(band_740 + band_705 + 0.16)
  tcari <- 3*((band_740 - band_705) - 0.2*(band_740 - band_560)*band_740/band_705)
  return(tcari/osavi)
}
REP <- function(sentinel){
  band_705 <- sentinel$rededge1
  band_665 <- sentinel$red
  band_740 <- sentinel$rededge2
  band_783 <- sentinel$rededge3
  REP <- 705 + 35*((band_665 + band_783)/2-band_705)/(band_740-band_705)
  return(REP)
}
sccci.1 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge1 <- sentinel$rededge1
  band_red <- sentinel$red
  re.ndvi.1 <- (band_nir - band_rededge1)/(band_nir + band_rededge1)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.1/ndvi)
}
sccci.2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge2 <- sentinel$rededge2
  band_red <- sentinel$red
  re.ndvi.2 <- (band_nir - band_rededge2)/(band_nir + band_rededge2)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.2/ndvi)
}
sccci.3 <- function(sentinel){
  band_nir <- sentinel$nir
  band_rededge3 <- sentinel$rededge3
  band_red <- sentinel$red
  re.ndvi.3 <- (band_nir - band_rededge3)/(band_nir + band_rededge3)
  ndvi <- (band_nir-band_red)/(band_nir+band_red)
  return(re.ndvi.3/ndvi)
}

```

#NDVI for the entire field overtime
```{r}
roop_ndvi_list <- lapply(roop_list, ndvi)

#dev.off()
par(mfrow=c(2,3))
for(i in 1:5){
  hist(raster::mask(roop_ndvi_list[[i]],wal_field), main=paste(names(roop_ndvi_list)[i],"NDVI of the field"),xlim=c(0.4,1.0),ylim=c(0,150),xlab="")
}

par(mfrow=c(1,1))
sapply(roop_ndvi_list, function(x) extract(x,y=wal_field, fun=mean))
sapply(roop_ndvi_list, function(x) extract(x,y=wal_field, fun=median))

```

# The function to generate a data frame of reflectance and vegetation indices
```{r}
df_reflectance <- function(locations_method){

  for(i in 1:length(locations_method)){
    #change the value of reflectance (divided by 10000)
    locations_method[[i]][,-1] <- locations_method[[i]][-1]/10000
    
    #add new columns of vegetation indices
    ##ndvi
    locations_method[[i]]$ndvi <- ndvi(locations_method[[i]])
    #gci
    locations_method[[i]]$gci <- gci(locations_method[[i]])
    ##grvi1
    locations_method[[i]]$grvi1 <- grvi1(locations_method[[i]])
    ##gndvi
    locations_method[[i]]$gndvi <- gndvi(locations_method[[i]])
    ##sr
    locations_method[[i]]$sr <- sr(locations_method[[i]])
    ##sr.green
    locations_method[[i]]$sr.green <- sr.green(locations_method[[i]])
    ##cvi
    locations_method[[i]]$cvi <- cvi(locations_method[[i]])
    ##savi
    locations_method[[i]]$savi <- savi(locations_method[[i]])
    ##psri.nir
    locations_method[[i]]$psri.nir <- psri.nir(locations_method[[i]])
    ##ndvi.green
    locations_method[[i]]$ndvi.green <- ndvi.green(locations_method[[i]])
    ##msavi2
    locations_method[[i]]$msavi2 <- msavi2(locations_method[[i]])
    ##lai.savi
    locations_method[[i]]$lai.savi <- lai.savi(locations_method[[i]])
    ##cri
    locations_method[[i]]$cri1 <- cri1(locations_method[[i]])
    ##arvi
    locations_method[[i]]$arvi <- arvi(locations_method[[i]])
    ##ari2
    locations_method[[i]]$ari2 <- ari2(locations_method[[i]])
    ##ndwi
    locations_method[[i]]$ndwi <- ndwi(locations_method[[i]])
    ##re.ndwi
    locations_method[[i]]$re.ndwi <- re.ndwi(locations_method[[i]])
    ##re.ndvi.1
    locations_method[[i]]$re.ndvi.1 <- re.ndvi.1(locations_method[[i]])
    ##re.ndvi.2
    locations_method[[i]]$re.ndvi.2 <- re.ndvi.2(locations_method[[i]])
    ##re.ndvi.3
    locations_method[[i]]$re.ndvi.3 <- re.ndvi.3(locations_method[[i]])
    ##psri
    locations_method[[i]]$psri <- psri(locations_method[[i]])
    ##ndre.1
    locations_method[[i]]$ndre.1 <- ndre.1(locations_method[[i]])
    ##ndre.2
    locations_method[[i]]$ndre.2 <- ndre.2(locations_method[[i]])
    ##ndre.3
    locations_method[[i]]$ndre.3 <- ndre.3(locations_method[[i]])
    ##ndi.45
    locations_method[[i]]$ndi.45 <- ndi.45(locations_method[[i]])
    ##mtci
    locations_method[[i]]$mtci <- mtci(locations_method[[i]])
    ##msi
    locations_method[[i]]$msi <- msi(locations_method[[i]])
    ##mcari
    locations_method[[i]]$mcari <- mcari(locations_method[[i]])
    ##ireci
    locations_method[[i]]$ireci <- ireci(locations_method[[i]])
    ##ci.rededge
    locations_method[[i]]$ci.rededge <- ci.rededge(locations_method[[i]])
    ##ci.green
    locations_method[[i]]$ci.green <- ci.green(locations_method[[i]])
    ##cri2
    locations_method[[i]]$cri2 <- cri2(locations_method[[i]])
    ##chl.rededge.1
    locations_method[[i]]$chl.rededge.1 <- chl.rededge.1(locations_method[[i]])
    ##chl.rededge.2
    locations_method[[i]]$chl.rededge.2 <- chl.rededge.2(locations_method[[i]])
    ##chl.rededge.3
    locations_method[[i]]$chl.rededge.3 <- chl.rededge.3(locations_method[[i]])
    ##ari1
    locations_method[[i]]$ari1 <- ari1(locations_method[[i]])
    ##tcari.osavi
    locations_method[[i]]$tcari.osavi <- tcari.osavi(locations_method[[i]])
    ##mcari.osavi
    locations_method[[i]]$mcari.osavi <- mcari.osavi(locations_method[[i]])
    ##mcari.osavi.705
    locations_method[[i]]$mcari.osavi.705 <- mcari.osavi.705(locations_method[[i]])
    ##tcari.osavi.705
    locations_method[[i]]$tcari.osavi.705 <- tcari.osavi.705(locations_method[[i]])
    ##REP
    locations_method[[i]]$REP <- REP(locations_method[[i]])
    ##sccci.1
    locations_method[[i]]$sccci.1 <- sccci.1(locations_method[[i]])
    ##sccci.2
    locations_method[[i]]$sccci.2 <- sccci.2(locations_method[[i]])
    ##sccci.3
    locations_method[[i]]$sccci.3 <- sccci.3(locations_method[[i]])
  }
  names(locations_method) <- as.Date.character(names(locations_method), format = "%Y%m%d")
  return(locations_method)
}
```

#Use of df_reflectance function to calculate vegetation index
```{r}
#drop 20170831 data
#WalSen_centers_sim$`20170831` <- NULL
#WalSen_centers_bil$`20170831` <- NULL
df_roop_20m <- df_reflectance(roop_centers_sim)
```

#integrate with swp data
##integrate_swp function
```{r}
integrate_swp <- function(df_locations_method, locations){
  if (locations == "points"){
    locations_method_select <- list()
    for(i in 1:length(df_locations_method)){
      #match the date
      swp_select <- swp_sen_datelist[[which(names(swp_sen_datelist) == names(df_locations_method)[i])]]
      #merge two data frame
      locations_method_select[[i]] <- merge(df_locations_method[[i]], swp_select, by = "ID", sort = TRUE)
    }
  }
  else if(locations == "centers" | locations == "blocks"){
    locations_method_select <- list()
    for(i in 1:length(df_locations_method)){
      #match the date with swp.ave_sen_datelist
      swp_select <- swp.ave_sen_datelist[[which(names(swp.ave_sen_datelist) == names(df_locations_method)[i])]]
      #merge two data frame
      locations_method_select[[i]] <- merge(df_locations_method[[i]], swp_select, by = "ID", sort = TRUE)
    }
  }
  names(locations_method_select) <- names(df_locations_method)
  return(locations_method_select)
}
```

##integration of swp data and sentinel data
```{r}
#drop 20170831 data
#swp.ave_sen_datelist$`2017-08-31` <- NULL
#swp_sen_datelist$`2017-08-31` <- NULL

#we have 5 dates of data left
swp_roop_20m <- integrate_swp(df_roop_20m, locations = "centers")

```

##integration of weather data
```{r}
#path_weather <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection"
path_weather <- "G:/CITRIS Project/Walnut_weather"
weather_roop <- read.csv(file.path(path_weather,"2017 roop walnut weather.csv"), header = TRUE)

#change the date format
weather_roop$date <- as.Date(weather_roop$date, format = "%m/%d/%Y")

weather_roop$date

#integration with swp_roop_20m
for(i in 1:length(swp_roop_20m)){
  #match the dates
  weather_select <- weather_roop[which(as.character(weather_roop$date) == names(swp_roop_20m)[i]),]
  swp_roop_20m[[i]] <- merge(swp_roop_20m[[i]], weather_select, by = "date")
}


```

#create a big data frame and output the csv
```{r}
#combine the sublists
roop_2017_20m <- do.call(rbind, swp_roop_20m)
rownames(roop_2017_20m) <- NULL

#output the csv
path_output <- "G:/CITRIS Project/Results"
write.csv(roop_2017_20m, file = file.path(path_output, "roop_2017_20m.csv"), col.names = TRUE, row.names = FALSE)


```


#Spectral unmixing 