---
title: "sentinel model building with match dates"
author: "Zhehan"
date: "November 16, 2017"
output: html_document
---
```{r}
library(leaps)
library(caret)
library(car)
library(MASS)
```


#read csv
```{r}
path_wal_sen <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection/sentinel with match dates"

ws_cb_df <- read.csv(file.path(path_wal_sen,"ws_cb_df.csv"), header=TRUE)
ws_cs_df <- read.csv(file.path(path_wal_sen,"ws_cs_df.csv"), header=TRUE)

#change the type of some columns 
ws_cs_df$irrigation <- as.factor(ws_cs_df$irrigation)
ws_cs_df$ID <- as.factor(ws_cs_df$ID)
ws_cs_df$rep <- as.factor(ws_cs_df$rep)
ws_cs_df$date <- as.factor(ws_cs_df$date)

ws_cb_df$irrigation <- as.factor(ws_cb_df$irrigation)
ws_cb_df$ID <- as.factor(ws_cb_df$ID)
ws_cb_df$rep <- as.factor(ws_cb_df$rep)
ws_cb_df$date <- as.factor(ws_cb_df$date)

dim(ws_cs_df)
str(ws_cs_df)
#produce a data frame that contains only numeric data
ws_cs_df_num <- select_if(ws_cs_df, is.numeric)
ws_cb_df_num <- select_if(ws_cb_df, is.numeric)
```

#the function to classify swp to 4 groups 
```{r}

swp.max = max(ws_cs_df$swp)
swp.min = min(ws_cs_df$swp)
swp.max
swp.min
swp_classification <- function(swp){
  swp_class <- cut(swp, breaks = c(swp.max, -4, -6, -8, -14),  labels = 4:1)
  return(swp_class)
}

swp_classification.2 <- function(swp){
  swp_class <- cut(swp, breaks = c(swp.max, -4, -6, -14), labels = 3:1)
  return(swp_class)
}

```

##filter one: correlation with swp
```{r}
#p-value of correlation with swp
p_cs <- apply(ws_cs_df[,c(3:55,61,62)],2,function(x) anova(lm(ws_cs_df$swp~x))$`Pr(>F)`[1])
#r-square of correlation with swp
r_cs <- apply(ws_cs_df[,c(3:55,61,62)],2,function(x) summary(lm(ws_cs_df$swp~x))$r.squared)


#p-value of correlation with swp.bs
p_cs.bs <- apply(ws_cs_df[,c(3:55,61,62)],2,function(x) anova(lm(ws_cs_df$swp.bs~x))$`Pr(>F)`[1])
#r-square of correlation with swp.bs
r_cs.bs <- apply(ws_cs_df[,c(3:55,61,62)],2,function(x) summary(lm(ws_cs_df$swp.bs~x))$r.squared)

#apply this filter
X_cs_filter1 <- ws_cs_df[,c(3:55,61,62)][,which(p_cs < 0.05)]
dim(ws_cs_df)
dim(X_cs_filter1)

p_cb <- apply(ws_cb_df[,c(3:55,61,62)],2,function(x) anova(lm(ws_cb_df$swp~x))$`Pr(>F)`[1])
r_cb <- apply(ws_cb_df[,c(3:55,61,62)],2,function(x) summary(lm(ws_cb_df$swp~x))$r.squared)
#apply this filter
X_cb_filter1 <- ws_cb_df[,c(3:55,61,62)][,which(p_cb < 0.05)]
dim(ws_cb_df)
dim(X_cb_filter1)


```

#rfe feature selection: backward selection 
```{r}
#set control, 3 repeat 10 cross validation 
set.seed(777)
rfecontrol_walsen <- rfeControl(functions = rfFuncs, method = "repeatedcv", number = 10, repeats = 3)
rfesubsets <- c(4,6,8,10,15,20,25,30,35,40,45,50,55)
#center simple
rfe_ws_cs_swp <- rfe(x =  ws_cs_df[,c(3:56, 61, 62)], y = ws_cs_df$swp, rfeControl = rfecontrol_walsen, sizes = rfesubsets,metric = 'Rsquared')
#center bilinear
rfe_ws_cb_swp <- rfe(x =  ws_cb_df[,c(3:56, 61, 62)], y = ws_cb_df$swp, rfeControl = rfecontrol_walsen, sizes = rfesubsets,metric = 'Rsquared')
#use baseline swp, center simple
rfe_ws_cs_swpbs <- rfe(x =  ws_cs_df[,c(3:56, 61, 62)], y = ws_cs_df$swp.bs, rfeControl = rfecontrol_walsen,sizes = rfesubsets, metric = 'Rsquared')
#use baseline swp, center bilinear
rfe_ws_cb_swpbs <- rfe(x =  ws_cb_df[,c(3:56, 61, 62)], y = ws_cb_df$swp.bs, rfeControl = rfecontrol_walsen,sizes = rfesubsets, metric = 'Rsquared')

#check the results
rfe_ws_cs_swp
predictors(rfe_ws_cs_swp)
rfe_ws_cb_swp
predictors(rfe_ws_cb_swp)
rfe_ws_cs_swpbs
predictors(rfe_ws_cs_swpbs)
rfe_ws_cb_swpbs
predictors(rfe_ws_cb_swpbs)

par(mfrow = c(2,2))
plot(rfe_ws_cs_swp, type = 'b', main = "SWP center simple", ylim = c(0.25,0.5))
plot(rfe_ws_cb_swp, type = 'b', main = "SWP center bilinear", ylim = c(0.25,0.5))
plot(rfe_ws_cs_swpbs, type = 'b', main = "SWP.bs center simple", ylim = c(0.25,0.5))
plot(rfe_ws_cb_swpbs, type = 'b', main = "SWP.bs center bilinear", ylim = c(0.25,0.5))
#rfe_cs_new <- rfe(x = X_cs_new_filter1, y=df_cs_new$swp, rfeControl = rfecontrol_cs_new)
```


##multiple linear regression with all data
```{r}
mlr_full_cs <- lm(ws_cs_df$swp~., data=ws_cs_df[,2:55])
mlr_full_cb <- lm(ws_cb_df$swp~., data=ws_cb_df[,2:55])

summary(mlr_full_cs)
summary(mlr_full_cb)
plot(mlr_full_cs)
vif(mlr_full_cs)

#regfit_cs <- regsubsets(y=ws_cs_df$swp,x=ws_cs_df[,c(3:55, 61, 62)], nvmax = 7, method="backward", really.big = TRUE)
#regfit_cb <- regsubsets(y=ws_cb_df$swp,x=X_cb_filter1, nvmax = 10,method="backward")
```

#10 fold validation, set training and testing data set
```{r}
set.seed(777)
#cross validatoin
fitControl <- trainControl(method = 'repeatedcv', number = 10, repeats = 3)
#training data and testing data
#train_test_split <- createDataPartition(swp_classification(ws_cs_df$swp),p=0.7,list=FALSE)
#cs_train <- ws_cs_df[train_test_split, ]
#cs_test <- ws_cs_df[-train_test_split,]
#cb_train <- ws_cb_df[train_test_split,]
#cb_test <- ws_cb_df[-train_test_split,]
```

##linear regression 
```{r}
slr_cs.scale <- train(swp~., data=ws_cs_df[,c(3:56,59, 61, 62)], method='lm', trControl=fitControl,preProc = c('scale','center'))
slr_cs <- train(swp~., data=ws_cs_df[,c(3:56,59, 61, 62)], method='lm', trControl=fitControl)

slr_cs.pred <- predict(slr_cs, cs_test[,c(2:55)])

slr_cb <- train(swp~., data=cb_train[,c(2:56,59)], method='lm', trControl=fitControl,preProc = c('scale','center'))
slr_cb.pred <- predict(slr_cb, cb_test[,c(2:55)])

slr_cs_swpbs <- train(swp.bs~., data=cs_train[,c(2:55,60)], method='lm', trControl=fitControl,preProc = c('scale','center'))
slr_cs_swpbs.pred <- predict(slr_cs_swpbs, cs_test[,c(2:55)])

slr_cb_swpbs <- train(swp.bs~., data=cb_train[,c(2:55,60)], method='lm', trControl=fitControl,preProc = c('scale','center'))
slr_cb_swpbs.pred <- predict(slr_cb_swpbs, cb_test[,c(2:55)])

mean((slr_cs.pred-cs_test$swp)^2)
summary(lm(slr_cs.pred~cs_test$swp))$r.squared

mean((slr_cb.pred-cb_test$swp)^2)
summary(lm(slr_cb.pred~cb_test$swp))$r.squared

mean((slr_cs_swpbs.pred-cs_test$swp.bs)^2)
summary(lm(slr_cs_swpbs.pred~cs_test$swp.bs))$r.squared

mean((slr_cb_swpbs.pred-cb_test$swp.bs)^2)
summary(lm(slr_cb_swpbs.pred~cb_test$swp))$r.squared

par(mfrow=c(2,2))
plot(slr_cs.pred, cs_test$swp, xlab = 'predicted swp', ylab="observed swp", main="SLR CS SWP", xlim = c(-10,2))
plot(slr_cb.pred, cb_test$swp, xlab = 'predicted swp', ylab="observed swp", main="SLR CB SWP", xlim = c(-10,2))
plot(slr_cs_swpbs.pred, cs_test$swp.bs, xlab = 'predicted swp.bs', ylab="observed swp", main="SLR CS SWP.BS", xlim = c(-6,6))
plot(slr_cb_swpbs.pred, cb_test$swp.bs, xlab = 'predicted swp', ylab="observed swp", main="SLR CS SWP.BS", xlim = c(-6,6))
```



##ridge regression
```{r}
#tune parameters 
lambdaGrid <- expand.grid(lambda = 10^seq(3,-3,length=100))

#ridge regression for cs
ridge_cs <- train(swp~., data=ws_cs_df[,c(3:56,59,61,62)], method='ridge',trControl=fitControl, tuneGrid = lambdaGrid, preProcess = c('center','scale'))
ridge_cs$bestTune
predict(ridge_cs$finalModel, type='coef', mode="norm")$coefficients[10,]
#ridge_cs.pred <- predict(ridge_cs, cs_test[,c(2:55)])
#sqrt(mean(ridge_cs.pred-cs_test$swp)^2)
#summary(lm(ridge_cs.pred~cs_test$swp))$r.squared


#ridge regression for cb
ridge_cb <- train(swp~., data=ws_cb_df[,c(3:56,59,61,62)], method='ridge',trControl=fitControl, tuneGrid = lambdaGrid, preProcess = c('center','scale'))
ridge_cb$bestTune
predict(ridge_cb$finalModel, type='coef', mode="norm")$coefficients[10,]
#ridge_cb.pred <- predict(ridge_cb, cb_test[,c(2:55)])
#sqrt(mean(ridge_cb.pred-cb_test$swp)^2)
#summary(lm(ridge_cb.pred~cb_test$swp))$r.squared


#ridge regression for cs swpbs
ridge_cs_swpbs <- train(swp.bs~., data=ws_cs_df[,c(3:56,60,61,62)], method='ridge',trControl=fitControl, tuneGrid = lambdaGrid, preProcess = c('center','scale'))
ridge_cs_swpbs$bestTune
predict(ridge_cs_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]
#ridge_cs_swpbs.pred <- predict(ridge_cs_swpbs, cs_test[,c(2:55)])
#sqrt(mean(ridge_cs_swpbs.pred-cs_test$swp.bs)^2)
#summary(lm(ridge_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#ridge regression for cb swpbs
ridge_cb_swpbs <- train(swp.bs~., data=ws_cb_df[,c(3:56,60,61,62)], method='ridge',trControl=fitControl, tuneGrid = lambdaGrid, preProcess = c('center','scale'))
ridge_cb_swpbs$bestTune
predict(ridge_cb_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]
#ridge_cb_swpbs.pred <- predict(ridge_cb_swpbs, cs_test[,c(2:55)])
#sqrt(mean(ridge_cb_swpbs.pred-cb_test$swp.bs)^2)
#summary(lm(ridge_cb_swpbs.pred~cb_test$swp.bs))$r.squared


#mean((ridge_cs.pred-cs_test$swp)^2)
#summary(lm(ridge_cs.pred~cs_test$swp))$r.squared

#mean((ridge_cb.pred-cb_test$swp)^2)
#summary(lm(ridge_cb.pred~cb_test$swp))$r.squared

#mean((ridge_cs_swpbs.pred-cs_test$swp.bs)^2)
#summary(lm(ridge_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#mean((ridge_cb_swpbs.pred-cb_test$swp.bs)^2)
#summary(lm(ridge_cb_swpbs.pred~cb_test$swp))$r.squared

#par(mfrow=c(2,2))
#plot(ridge_cs.pred, cs_test$swp, xlab = 'predicted swp', ylab="observed swp", main="ridge CS SWP", xlim = c(-8,-2))
#plot(ridge_cb.pred, cb_test$swp, xlab = 'predicted swp', ylab="observed swp", main="ridge CB SWP", xlim = c(-8,-2))
#plot(ridge_cs_swpbs.pred, cs_test$swp.bs, xlab = 'predicted swp.bs', ylab="observed swp", main="ridge CS SWP.BS", xlim = c(-4,2))
#plot(ridge_cb_swpbs.pred, cb_test$swp.bs, xlab = 'predicted swp', ylab="observed swp", main="ridge CS SWP.BS", xlim = c(-4,2))
```

#lasso regression
```{r}
#tune parameters 
#lambdaGrid <- expand.grid(lambda = 10^seq(3,-3,length=100))

#lasso regression for cs
lasso_cs <- train(swp~., data=ws_cs_df[,c(3:56,59,61,62)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#lasso_cs.pred <- predict(lasso_cs, cs_test[,c(2:55)])
#sqrt(mean(lasso_cs.pred-cs_test$swp)^2)
#summary(lm(lasso_cs.pred~cs_test$swp))$r.squared


#lasso regression for cb
lasso_cb <- train(swp~., data=ws_cb_df[,c(3:56,59,61,62)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#lasso_cb.pred <- predict(lasso_cb, cb_test[,c(2:55)])
#sqrt(mean(lasso_cb.pred-cb_test$swp)^2)
#summary(lm(lasso_cb.pred~cb_test$swp))$r.squared


#lasso regression for cs
lasso_cs_swpbs <- train(swp.bs~., data=ws_cs_df[,c(3:56,60,61,62)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#lasso_cs_swpbs.pred <- predict(lasso_cs_swpbs, cs_test[,c(2:55)])
#sqrt(mean(lasso_cs_swpbs.pred-cs_test$swp.bs)^2)
#summary(lm(lasso_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#lasso regression for cb
lasso_cb_swpbs <- train(swp.bs~., data=ws_cb_df[,c(3:56,60,61,62)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#lasso_cb_swpbs.pred <- predict(lasso_cb_swpbs, cs_test[,c(2:55)])
#sqrt(mean(lasso_cb_swpbs.pred-cb_test$swp.bs)^2)
#summary(lm(lasso_cb_swpbs.pred~cb_test$swp.bs))$r.squared


#mean((lasso_cs.pred-cs_test$swp)^2)
#summary(lm(lasso_cs.pred~cs_test$swp))$r.squared

#mean((lasso_cb.pred-cb_test$swp)^2)
#summary(lm(lasso_cb.pred~cb_test$swp))$r.squared

#mean((lasso_cs_swpbs.pred-cs_test$swp.bs)^2)
#summary(lm(lasso_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#mean((lasso_cb_swpbs.pred-cb_test$swp.bs)^2)
#summary(lm(lasso_cb_swpbs.pred~cb_test$swp))$r.squared

#par(mfrow=c(2,2))
#plot(lasso_cs.pred, cs_test$swp, xlab = 'predicted swp', ylab="observed swp", main="lasso CS SWP", xlim = c(-8,-2))
#plot(lasso_cb.pred, cb_test$swp, xlab = 'predicted swp', ylab="observed swp", main="lasso CB SWP", xlim = c(-8,-2))
#plot(lasso_cs_swpbs.pred, cs_test$swp.bs, xlab = 'predicted swp.bs', ylab="observed swp", main="lasso CS SWP.BS", xlim = c(-4,2))
#plot(lasso_cb_swpbs.pred, cb_test$swp.bs, xlab = 'predicted swp', ylab="observed swp", main="lasso CS SWP.BS", xlim = c(-4,2))

lasso_cs$bestTune
lasso_cb$bestTune
lasso_cs_swpbs$bestTune
lasso_cb_swpbs$bestTune

lasso_cs
predict(lasso_cs$finalModel, type='coef', mode="norm")$coefficients[10,]

lasso_cb
predict(lasso_cb$finalModel, type='coef', mode="norm")$coefficients[10,]

lasso_cs_swpbs
predict(lasso_cs_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]

lasso_cb_swpbs
predict(lasso_cb_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]

```

##PCR: principle components regression
```{r}
#pcr regression for cs
pcr_cs <- train(swp~., data=cs_train[,c(2:55,59)], method='pcr',trControl=fitControl, preProcess = c('center','scale'))
pcr_cs.pred <- predict(pcr_cs, cs_test[,c(2:55)])
sqrt(mean(pcr_cs.pred-cs_test$swp)^2)
summary(lm(pcr_cs.pred~cs_test$swp))$r.squared


#pcr regression for cb
pcr_cb <- train(swp~., data=cb_train[,c(2:55,59)], method='pcr',trControl=fitControl, preProcess = c('center','scale'))
pcr_cb.pred <- predict(pcr_cb, cb_test[,c(2:55)])
sqrt(mean(pcr_cb.pred-cb_test$swp)^2)
summary(lm(pcr_cb.pred~cb_test$swp))$r.squared


#pcr regression for cs
pcr_cs_swpbs <- train(swp.bs~., data=cs_train[,c(2:55,60)], method='pcr',trControl=fitControl, preProcess = c('center','scale'))
pcr_cs_swpbs.pred <- predict(pcr_cs_swpbs, cs_test[,c(2:55)])
sqrt(mean(pcr_cs_swpbs.pred-cs_test$swp.bs)^2)
summary(lm(pcr_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#pcr regression for cb
pcr_cb_swpbs <- train(swp.bs~., data=cb_train[,c(2:55,60)], method='pcr',trControl=fitControl,  preProcess = c('center','scale'))
pcr_cb_swpbs.pred <- predict(pcr_cb_swpbs, cs_test[,c(2:55)])
sqrt(mean(pcr_cb_swpbs.pred-cb_test$swp.bs)^2)
summary(lm(pcr_cb_swpbs.pred~cb_test$swp.bs))$r.squared


mean((pcr_cs.pred-cs_test$swp)^2)
summary(lm(pcr_cs.pred~cs_test$swp))$r.squared

mean((pcr_cb.pred-cb_test$swp)^2)
summary(lm(pcr_cb.pred~cb_test$swp))$r.squared

mean((pcr_cs_swpbs.pred-cs_test$swp.bs)^2)
summary(lm(pcr_cs_swpbs.pred~cs_test$swp.bs))$r.squared

mean((pcr_cb_swpbs.pred-cb_test$swp.bs)^2)
summary(lm(pcr_cb_swpbs.pred~cb_test$swp))$r.squared

par(mfrow=c(2,2))
plot(pcr_cs.pred, cs_test$swp, xlab = 'predicted swp', ylab="observed swp", main="pcr CS SWP", xlim = c(-7,-4))
plot(pcr_cb.pred, cb_test$swp, xlab = 'predicted swp', ylab="observed swp", main="pcr CB SWP", xlim = c(-7,-4))
plot(pcr_cs_swpbs.pred, cs_test$swp.bs, xlab = 'predicted swp.bs', ylab="observed swp", main="pcr CS SWP.BS", xlim = c(-2,1))
plot(pcr_cb_swpbs.pred, cb_test$swp.bs, xlab = 'predicted swp', ylab="observed swp", main="pcr CS SWP.BS", xlim = c(-2,1))

```
```{r}
```



##PLS: partial least squares
```{r}
#pls regression for cs
pls_cs <- plsr(swp~., data=cs_train[,c(2:55,59)],scale=TRUE, validation ="CV")
#pls_cs <- train(swp~., data=cs_train[,c(2:55,59)], method='pls',trControl=fitControl, tuneLength=5, preProcess = c('center','scale'))
validationplot(pls_cs, val.type = 'MSEP')
pls_cs.pred <- predict(pls_cs, cs_test[,c(2:55)])
sqrt(mean(pls_cs.pred-cs_test$swp)^2)
summary(lm(pls_cs.pred~cs_test$swp))$r.squared


#pls regression for cb
pls_cb <- plsr(swp~., data=cb_train[,c(2:55,59)],scale=TRUE, validation ="CV")
#pls_cb <- train(swp~., data=cb_train[,c(2:55,59)], method='pls',trControl=fitControl, tuneLength=5, preProcess = c('center','scale'))
pls_cb.pred <- predict(pls_cb, cb_test[,c(2:55)])
sqrt(mean(pls_cb.pred-cb_test$swp)^2)
summary(lm(pls_cb.pred~cb_test$swp))$r.squared


#pls regression for cs
pls_cs_swpbs <- plsr(swp.bs~., data=cs_train[,c(2:55,60)],scale=TRUE, validation ="CV")
#pls_cs_swpbs <- train(swp.bs~., data=cs_train[,c(2:55,60)], method='pls',trControl=fitControl, tuneLength=5, preProcess = c('center','scale'))
pls_cs_swpbs.pred <- predict(pls_cs_swpbs, cs_test[,c(2:55)])
sqrt(mean(pls_cs_swpbs.pred-cs_test$swp.bs)^2)
summary(lm(pls_cs_swpbs.pred~cs_test$swp.bs))$r.squared

#pls regression for cb
pls_cb_swpbs <- plsr(swp.bs~., data=cb_train[,c(2:55,60)],scale=TRUE, validation="CV")
#pls_cb_swpbs <- train(swp.bs~., data=cb_train[,c(2:55,60)], method='pls',trControl=fitControl, tuneLength=5, preProcess = c('center','scale'))
pls_cb_swpbs.pred <- predict(pls_cb_swpbs, cs_test[,c(2:55)])
sqrt(mean(pls_cb_swpbs.pred-cb_test$swp.bs)^2)
summary(lm(pls_cb_swpbs.pred~cb_test$swp.bs))$r.squared

```

#random forest regression 
```{r}
#train with random forest regression model
lasso_cs <- train(swp~., data=ws_cs_df[,c(3:56,59,61,62)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))

#fit the model
rf_ws_cs <- train(x = ws_cs_df[,c(3:56,61,62)], y=ws_cs_df$swp, method = "rf", trControl = fitControl, tuneLength = 10, preProcess = c('center','scale'), importance = TRUE)
rf_ws_cb <- train(x = ws_cb_df[,c(3:56,61,62)], y=ws_cb_df$swp, method = "rf", trControl = fitControl, tuneLength = 10, preProcess = c('center','scale'), importance = TRUE)
rf_ws_cs_swpbs <- train(x = ws_cs_df[,c(3:56,61,62)], y=ws_cs_df$swp.bs, method = "rf", trControl = fitControl, tuneLength = 10, preProcess = c('center','scale'), importance = TRUE)
rf_ws_cb_swpbs <- train(x = ws_cs_df[,c(3:56,61,62)], y=ws_cb_df$swp.bs, method = "rf", trControl = fitControl, tuneLength = 10, preProcess = c('center','scale'), importance = TRUE)

#importance
rf_ws_cs
varImp(rf_ws_cs)

rf_ws_cb
varImp(rf_ws_cb)

rf_ws_cs_swpbs
varImp(rf_ws_cs_swpbs)

rf_ws_cb_swpbs
varImp(rf_ws_cb_swpbs)

```


#random forest classification
```{r}
set.seed(777)
rf.class_ws_cs <- train(x = ws_cs_df[,c(3:56,61,62)], y=swp_classification(ws_cs_df$swp), method = "rf", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)

rf.class_ws_cb <- train(x = ws_cb_df[,c(3:56,61,62)], y=swp_classification(ws_cb_df$swp), method = "rf", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)

rf.class2_ws_cs <- train(x = ws_cs_df[,c(3:56,61,62)], y=swp_classification.2(ws_cs_df$swp), method = "rf", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)

rf.class2_ws_cb <- train(x = ws_cb_df[,c(3:56,61,62)], y=swp_classification.2(ws_cb_df$swp), method = "rf", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)


rf.class_ws_cs
rf.class_ws_cb
rf.class2_ws_cs
rf.class2_ws_cb
varImp(rf.class_ws_cs)
varImp(rf.class_ws_cb)
varImp(rf.class2_ws_cs)
varImp(rf.class2_ws_cb)

confusionMatrix(rf.class_ws_cs)
confusionMatrix(rf.class_ws_cb)
confusionMatrix(rf.class2_ws_cs)
confusionMatrix(rf.class2_ws_cb)

```

#svm classification
```{r}
svm.class_ws_cs <-  train(x = ws_cs_df[,c(3:56,61,62)], y=swp_classification(ws_cs_df$swp), method = "svmLinear", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)

svm.class2_ws_cs <-  train(x = ws_cs_df[,c(3:56,61,62)], y=swp_classification.2(ws_cs_df$swp), method = "svmLinear", preProcess = c("center","scale"), trControl = fitControl, importance = TRUE)

varImp(svm.class_ws_cs)

```

