---
title: "Walnut UAV data analysis"
author: "Zhehan"
date: "November 1, 2017"
output: html_document
---

#prepare 
```{r}
library(raster)
library(caret)
```


```{r}
read_uav <- function(path, red, green, blue, rededge, nir){
  #read raster layer
  uav_red <- raster(file.path(path, red))
  uav_green <- raster(file.path(path, green))
  uav_blue <- raster(file.path(path, blue))
  uav_rededge <- raster(file.path(path, rededge))
  uav_nir <- raster(file.path(path, nir))
  
  #brick the 5 bands 
  uav_brick <- brick(stack(uav_blue, uav_green, uav_red, uav_rededge, uav_nir))
  
  #rename the bands
  names(uav_brick) <- c("blue","green","red","rededge","nir")
  
  return(uav_brick)
}
```

#read uav image
```{r}
uav_20170711 <- read_uav(path = "G:/CITRIS Project/Walnut_UAV/20170711 Tehama walnut UAV/4_index/reflectance",
                         red = "20170711 tehama walnut uav_transparent_reflectance_red.tif", 
                         blue = "20170711 tehama walnut uav_transparent_reflectance_blue.tif",
                         green = "20170711 tehama walnut uav_transparent_reflectance_green.tif",
                         rededge = "20170711 tehama walnut uav_transparent_reflectance_rededge.tif",
                         nir = "20170711 tehama walnut uav_transparent_reflectance_nir.tif")

uav_20170724 <- read_uav(path = "G:/CITRIS Project/Walnut_UAV/20170724 Tehama walnut UAV/4_index/reflectance",
                         blue  = "20170724 tehama walnut uav_transparent_reflectance_blue.tif", 
                         green = "20170724 tehama walnut uav_transparent_reflectance_green.tif",
                         red = "20170724 tehama walnut uav_transparent_reflectance_red.tif",
                         rededge = "20170724 tehama walnut uav_transparent_reflectance_rededge.tif",
                         nir = "20170724 tehama walnut uav_transparent_reflectance_nir.tif")

uav_20170822 <- read_uav(path = "G:/CITRIS Project/Walnut_UAV/20170822 Tehama walnut UAV/4_index/reflectance",
                         blue  = "20170822 tehama walnut uav_transparent_reflectance_blue.tif", 
                         green = "20170822 tehama walnut uav_transparent_reflectance_green.tif",
                         red = "20170822 tehama walnut uav_transparent_reflectance_red.tif",
                         rededge = "20170822 tehama walnut uav_transparent_reflectance_rededge.tif",
                         nir = "20170822 tehama walnut uav_transparent_reflectance_nir.tif")

uav_20170711@extent
uav_20170711@ncols
uav_20170711@nrows
res(uav_20170711)
res(uav_20170724)
res(uav_20170822)
```

#plot uav image
```{r}
plotRGB(uav_20170711, 3, 2, 1, stretch = "lin" )
plot(MAP2_centers, add=TRUE, col='red')

plotRGB(uav_20170724, 3, 2, 1, stretch = "lin")
plot(MAP2_centers, add=TRUE, col='red')

plotRGB(uav_20170822, 3, 2, 1, stretch = "lin")
plot(MAP2_centers, add=TRUE, col='red')
```

#read the shapefile of MAP2 and MAP2_points
```{r}
path_boundary <- "G:/CITRIS Project/site locations/Shapefiles"
#this is the shapefile of the boundary of blocks
wal_blocks <- shapefile(file.path(path_boundary, "MAP2_blocks.shp"))

#use '_' to replace ' ' and ','
wal_blocks$Name <- gsub(x=gsub(x = wal_blocks$Name, replacement = '', pattern = ","),replacement ="_", pattern = " " )
#change grower's practice to 0_bar_below
wal_blocks$Name <- gsub(wal_blocks$Name, pattern = "Grower's_practice", replacement = "0_bar_below")

#unify the crs
wal_blocks <- spTransform(wal_blocks, crs(uav_20170711))

#remove the big boundary
wal_field <- wal_blocks[wal_blocks$Name == "2014_Tehama_Walnut_Irrigation_Treatment",]
wal_blocks <- wal_blocks[wal_blocks$Name != "2014_Tehama_Walnut_Irrigation_Treatment",]

```


#Read the shapefile of MAP2_points
```{r}
wal_points <- shapefile(file.path(path_boundary, "MAP2_points.shp"))
#use '_' to replace ' ' and ','
wal_points$Name <- gsub(x=gsub(x = wal_points$Name, replacement = '', pattern = ","),replacement ="_", pattern = " " )
#change grower's practice to 0_bar_below
wal_points$Name <- gsub(wal_points$Name, pattern = "Grower's_practice", replacement = "0_bar_below")
#change "3_bar" to "3_bars"
wal_points$Name <- gsub(wal_points$Name, pattern = "3_bar_", replacement = "3_bars_")
#change "4_bar" to "4_bars"
wal_points$Name <- gsub(wal_points$Name, pattern = "4_bar_", replacement = "4_bars_")
#remove extra dimension of coordinate system
wal_points@coords <- wal_points@coords[,1:2]
#unify the crs
wal_points <- spTransform(wal_points, crs(uav_20170711))

```


#create a new data frame of the spatial points data frame of the centers of two points in each block
```{r}
#Add a column of blocks to wal_points
wal_points$blocks <- sapply(strsplit(wal_points$Name, "_Tree",1),'[',1)
#split them by blocks so that we can have 
wal_centers_split <- split(wal_points, wal_points$blocks)
wal_centers_split <- lapply(wal_centers_split, function(x) SpatialPointsDataFrame(coords = matrix(colMeans(x@coords),1,2), proj4string = x@proj4string, data = data.frame(Name = unique(x$blocks))))

wal_centers <- do.call(rbind,wal_centers_split)
wal_centers$Name <- as.character(wal_centers$Name)

#-------------------------------------------------------#
#order it
wal_blocks <- wal_blocks[order(wal_blocks$Name),]
wal_centers <- wal_centers[order(wal_centers$Name),]
wal_points <- wal_points[order(wal_points$Name),]
wal_centers_buffer = buffer(wal_centers, 5)

#-------------------------------------------------------#
#plot it
plot(wal_field)
plot(wal_blocks, add = TRUE )
plot(wal_centers, add= TRUE, pch = 20, col = 'red')
plot(wal_points, add = TRUE)
plot(wal_centers_buffer, add = TRUE)


plot(wal_field)
plot(wal_centers_buffer, add = TRUE)

plot(wal_field)
plot(wal_blocks, add = TRUE)
plot(wal_blocks[wal_blocks$Name=="4_bars_below_Rep_5",], add = TRUE, col='red')
plot(wal_blocks[wal_blocks$Name=="4_bars_below_Rep_4",], add = TRUE, col='red')

```


#set NDVI threshold to tease out bare soil
```{r}
ndvi_uav_20170711 <- ndvi(uav_20170711)
ndvi_uav_20170724 <- ndvi(uav_20170724)
ndvi_uav_20170822 <- ndvi(uav_20170822)

#set threshold to be 0.7
veg_uav_20170711 <- calc(ndvi_uav_20170711, function(x){x[x<0.7]<-NA; return(x)})

veg_uav_20170724 <- calc(ndvi_uav_20170724, function(x){x[x<0.7]<-NA; return(x)})

veg_uav_20170822 <- calc(ndvi_uav_20170822, function(x){x[x<0.7]<-NA; return(x)})

plot(veg_uav_20170711)
plot(wal_centers, add = TRUE, col= 'red')

plot(veg_uav_20170724)
plot(wal_centers, add = TRUE, col= 'red')

plot(veg_uav_20170822)
plot(wal_centers, add = TRUE, col= 'red')

#mask out
uav_20170711_mask <- raster::mask(x=uav_20170711, mask=veg_uav_20170711)
plotRGB(uav_20170711_mask,3,2,1, stretch='lin')
plot(wal_centers, add = TRUE, col= 'red')

uav_20170724_mask <- raster::mask(x=uav_20170724, mask=veg_uav_20170724)
plotRGB(uav_20170724_mask,3,2,1, stretch='lin')
plot(wal_centers, add = TRUE, col= 'red')

uav_20170822_mask <- raster::mask(x=uav_20170822, mask=veg_uav_20170822)
plotRGB(uav_20170822_mask,3,2,1, stretch='lin')
plot(wal_centers, add = TRUE, col= 'red')
plot(wal_blocks, add = TRUE)

```

#extract reflectance
```{r}
#Extract function. It does not work due to something with buffer settings
extract_uav <- function(uav_image, MAP2_locations, buffer, method, fun){
  extract_ref <- raster::extract(x=uav_image, y = MAP2_locations, buffer, method, fun, df = TRUE, na.rm = TRUE)
  extract_ref$ID <- MAP2_locations$Name
  return(extract_ref)
}


#extract information
ref_uav_20170711 <- raster::extract(x=uav_20170711_mask, y=wal_centers, buffer = 5, fun=mean, na.rm = TRUE, df= TRUE)
ref_uav_20170711$ID <- wal_centers$Name

ref_uav_20170724 <- raster::extract(x=uav_20170724_mask, y=wal_centers, buffer = 5, fun =mean, na.rm=TRUE, df=TRUE)
ref_uav_20170724$ID <- wal_centers$Name


ref_uav_20170822 <- raster::extract(x=uav_20170822_mask, y=wal_centers, buffer = 5, fun =mean, na.rm=TRUE, df=TRUE)
ref_uav_20170822$ID <- wal_centers$Name

#remove the rows that is not covered by our plot
ref_uav_20170711 <- ref_uav_20170711[-c(1,6,9,16,22,23),]

```


#calculate some indices for micasense rededge
```{r}
ndvi <- function(uav){
  red <- uav$red
  nir <- uav$nir
  ndvi <- (nir-red)/(nir+red)
  return(ndvi)
}

ndre <- function(uav){
  nir <- uav$nir
  rededge <- uav$rededge
  ndre <- (nir-rededge)/(nir+rededge)
  return(ndre)
}

gndvi <- function(uav){
  green <- uav$green
  nir <- uav$nir
  gndvi <- (nir-green)/(nir+green)
  return(gndvi)
}

osavi <- function(uav){
  nir <- uav$nir
  red <- uav$red
  osavi <- (1+0.16)*(nir-red)/(nir+red+0.16)
}

grvi1 <- function(sentinel){
  band_red <- sentinel$red
  band_green <- sentinel$green
  grvi1 <- (band_red - band_green)/(band_red + band_green)
  return(grvi1)
}

evi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  evi <- (2.5*(band_nir-band_red)/(band_nir+6*band_red-7.5*band_blue+1))
  return(evi)
}

evi2 <- function(sentinel){
  band_red <- sentinel$red
  band_nir <- sentinel$nir
  evi2 <- 2.5*(band_nir-band_red)/(band_nir+2.4*band_red+1)
  return(evi2)
}

sr <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  sr <- band_nir/band_red
  return(sr)
}

sr.green <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  sr.green <- band_842/band_560
  return(sr.green)
}

cvi <- function(sentinel){
  band_842 <- sentinel$nir
  band_560 <- sentinel$green
  band_665 <- sentinel$red
  cvi <- (band_842/band_560)/(band_560+band_665)
  return(cvi)
}

savi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  savi <- 1.5*(band_nir-band_red)/(band_nir+band_red+0.5)
  return(savi)
}

psri.nir <- function(sentinel){
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  band_nir <- sentinel$nir
  psri.nir <- (band_red - band_blue)/(band_nir)
  return(psri.nir)
}

ndvi.green <- function(sentinel){
  band_green <- sentinel$green
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  ndvi.green <- band_green*(band_nir - band_red)/(band_nir + band_red)
  return(ndvi.green)
}

msavi2 <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  msavi2 <- (band_nir + 1) - 0.5*sqrt((2*band_nir - 1)^2 + 8*band_red)
  return(msavi2)
}

lai.savi <- function(sentinel){
  band_red <- sentinel$red 
  band_nir <- sentinel$nir
  lai.savi <- -log(0.371 + 1.5*(band_nir - band_red)/(band_nir + band_red + 0.5))/2.4
  return(lai.savi)
}

cri1 <- function(sentinel){
  band_green <- sentinel$green
  band_blue <- sentinel$blue
  cri1 <- (1/band_blue)-(1/band_green)
  return(cri1)
}

arvi <- function(sentinel){
  band_nir <- sentinel$nir
  band_red <- sentinel$red
  band_blue <- sentinel$blue
  arvi <- (band_nir - (2*band_red - band_blue))/(band_nir + (2*band_red-band_blue))
  return(arvi)
}

ari2 <- function(sentinel){
  band_nir <- sentinel$nir
  band_blue <- sentinel$blue
  band_green <- sentinel$green
  ari2 <- (band_nir/band_blue)-(band_nir/band_green)
  return(ari2)
}

re.ndwi <- function(uav){
  band_rededge <- uav$rededge
  band_green <- uav$green
  re.ndwi <- (band_green-band_rededge)/(band_green+band_rededge)
  return(re.ndwi)
}



```

```{r}
uav_indices <- function(uav){
  uav$ndvi <- ndvi(uav)
  uav$ndre <- ndre(uav)
  uav$re.ndwi <- re.ndwi(uav)
  uav$air2 <- ari2(uav)
  uav$arvi <- arvi(uav)
  uav$cri1 <- cri1(uav)
  uav$lai.savi <- lai.savi(uav)
  uav$msavi2 <- msavi2(uav)
  uav$ndvi.green <- ndvi.green(uav)
  uav$psri.nir <- psri.nir(uav)
  uav$savi <- savi(uav)
  uav$cvi <- cvi(uav)
  uav$sr.green <- sr.green(uav)
  uav$sr <- sr(uav)
  uav$evi2 <- evi2(uav)
  uav$evi <- evi(uav)
  uav$grvi1 <- grvi1(uav)
  uav$osavi <- osavi(uav)
  uav$gndvi <- gndvi(uav)
  return(uav)
}

df_uav_20170711 <- uav_indices(ref_uav_20170711)
df_uav_20170724 <- uav_indices(ref_uav_20170724)
df_uav_20170822 <- uav_indices(ref_uav_20170822)
```

#read swp data
```{r}
path_swp <- "G:/CITRIS Project/Walnut_SWP/2017 walnut swp raw data"
#path_swp <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection"
swp <- read.csv(file.path(path_swp, "20171013 walnut swp.csv"), header = TRUE)
#SELECT columns
swp <- dplyr::select(swp, Measure.ment.Date, Rep, Irrigation.Treatment.Code, Tree.., Orchard.SWP........bars.,Bars.Below.Base.Line)
#change the colname of the dataframe
colnames(swp) <- c("date", "rep", "irrigation", "tree", "swp", "swp.bs")
#change the date format
swp$date <- as.Date(swp$date, format = "%m/%d/%Y")

#change the name of irrigation 
swp$irrigation <- gsub(swp$irrigation, pattern = " ", replacement = "_")
swp$irrigation <- gsub(swp$irrigation, pattern = "Grower_Practice", replacement = "0_bar_below")

#add a new column of indiviudal tree
swp$ID <- paste(swp$irrigation,"Rep", swp$rep, "Tree", swp$tree, sep = "_")

#change the class of each column
swp$rep <- as.factor(swp$rep)
swp$irrigation <- as.factor(swp$irrigation)
swp$tree <- as.factor(swp$tree)
swp$ID <- as.factor(swp$ID)
#change the order of the data frame, making ID at the beginging
swp <- swp %>% dplyr::select(ID, everything())

head(swp)
tail(swp)

swp_ID_list <- split(swp, swp$ID)

```

```{r}
swp_uav <- subset(swp,date %in% as.Date(c('2017-07-11','2017-07-24','2017-08-22'))) 
dim(swp_uav)
#split with dates
swp_uav_datelist <- split(swp_uav, swp_uav$date)

#create an empty list to swp_ave
swp.ave_uav_datelist <- list()
for(i in 1:length(swp_uav_datelist)){
  #aggregate to calculate the average of swp from two trees in th same block
  swp.ave_uav_datelist[[i]] <- aggregate(x=swp_uav_datelist[[i]][6:7], by = list(date = swp_uav_datelist[[i]]$date, rep=swp_uav_datelist[[i]]$rep, irrigation = swp_uav_datelist[[i]]$irrigation), FUN = mean)
  #rename the fourth column from "x" to "swp"
  colnames(swp.ave_uav_datelist[[i]])[4] = "swp"
  #create a new column called "ID", which is the block name 
  swp.ave_uav_datelist[[i]]$ID <- paste(swp.ave_uav_datelist[[i]]$irrigation, "Rep", swp.ave_uav_datelist[[i]]$rep, sep = "_")
  #change the ID column from character to factor
  swp.ave_uav_datelist[[i]]$ID <- as.factor(swp.ave_uav_datelist[[i]]$ID)
  #make the ID column come to the front 
  #swp.ave_uav_datelist[[i]] <- swp.ave_uav_datelist[[i]] %>% dplyr::select(ID, everything())

  #name each sublist
  names(swp.ave_uav_datelist)[i] <- names(swp_uav_datelist)[i]

}

```

#integrate corresponding swp to the reflectance table
```{r}
df_uav_20170711 <- merge(df_uav_20170711, swp.ave_uav_datelist$`2017-07-11`, by = "ID", sort = TRUE)
df_uav_20170724 <- merge(df_uav_20170724, swp.ave_uav_datelist$`2017-07-24`, by = "ID", sort = TRUE)
df_uav_20170822 <- merge(df_uav_20170822, swp.ave_uav_datelist$`2017-08-22`, by = "ID", sort = TRUE)

```

#integrate weather data
```{r}
#path_weather <- "C:/Users/tangz/Box Sync/Zhehan/sentinel water stress detection"
path_weather <- "G:/CITRIS Project/Walnut_weather"
weather_wal <- read.csv(file.path(path_weather,"20171013 walnut weather.csv"), header = TRUE)

#change the date format
weather_wal$date <- as.Date(weather_wal$date, format = "%m/%d/%Y")

weather_wal$date

#integration with swp_WalSen_cs 
df_uav_20170711 <- merge(df_uav_20170711, weather_wal[which(as.character(weather_wal$date)== "2017-07-11"),], by = "date")
df_uav_20170724 <- merge(df_uav_20170724, weather_wal[which(as.character(weather_wal$date)== "2017-07-24"),], by = "date")
df_uav_20170822 <- merge(df_uav_20170822, weather_wal[which(as.character(weather_wal$date)== "2017-08-22"),], by = "date")

```

#combine three different dates
```{r}
wal_uav_df <- rbind(df_uav_20170711, df_uav_20170724, df_uav_20170822)
ggplot(data=wal_uav_df, aes(x=ndvi, y=swp))+geom_point(aes(color=factor(date)))

head(wal_uav_df) 

#output this data frame
path_uav <- "G:/CITRIS Project/Walnut_UAV"
write.csv(wal_uav_df, file = file.path(path_uav, "wal_uav_df.csv"), col.names = TRUE, row.names = FALSE)
```






#----------------------------------------Preprocessing--------------------------------------------#

#correlation with swp
```{r}
p_cs_uav <- apply(wal_uav_df[,c(3:26,31,32)],2,function(x) anova(lm(wal_uav_df$swp~x))$`Pr(>F)`[1])
#r-square of correlation with swp
r_cs_uav <- apply(wal_uav_df[,c(3:26,31,32)],2,function(x) summary(lm(wal_uav_df$swp~x))$r.squared)


#p-value of correlation with swp.bs
p_cs_uav.bs <- apply(wal_uav_df[,c(3:26,31,32)],2,function(x) anova(lm(wal_uav_df$swp.bs~x))$`Pr(>F)`[1])
#r-square of correlation with swp.bs
r_cs_uav.bs <- apply(wal_uav_df[,c(3:26,31,32)],2,function(x) summary(lm(wal_uav_df$swp.bs~x))$r.squared)

```

#filter 2: feature selection using rfe in caret package
```{r}
set.seed(777)
rfecontrol_uav <- rfeControl(functions = rfFuncs, method = "repeatedcv", number = 10, repeats = 3)
rfesubset <- c(4:10,15,20,25,26)

rfe_uav_1 <- rfe(x = X_uav_filter1, y=df_uav$swp, rfeControl = rfecontrol_uav, sizes = rfesubset, metric = "Rsquared")
rfe_uav_2 <- rfe(x = wal_uav_df[,c(3:26,31,32)], y=df_uav$swp, rfeControl = rfecontrol_uav, sizes = rfesubset, metric = "Rsquared")

rfe_uav_swpbs <- rfe(x = wal_uav_df[,c(3:26,31,32)], y=df_uav$swp.bs, rfeControl = rfecontrol_uav, sizes = rfesubset, metric = "Rsquared")


plot(rfe_uav_1, type = 'b')
plot(rfe_uav_2, type = 'b')

rfe_uav
rfe_uav$optVariables

#apply this filter
X_uav_filter2 <- X_uav_filter1[,rfe_uav_1$optVariables]
head(X_uav_filter2)
```

#fit control function 
```{r}
set.seed(777)
control_uav <- trainControl(method="repeatedcv", number = 10, repeats = 3)
```

#ridge regression 
```{r}
#tune parameters with tunelength=10
ridge_uav_swp <- train(swp~., data=wal_uav_df[,c(3:26,29,31,32)], method='ridge',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
predict(ridge_uav_swp$finalModel, type='coef', mode="norm")$coefficients[10,]


ridge_uav_swpbs <- train(swp.bs~., data=wal_uav_df[,c(3:26,30,31,32)], method='ridge',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#the coefficients
predict(ridge_uav_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]
```

#lasso regression 
```{r}
#tune parameters with tunelength=10
lasso_uav_swp <- train(swp~., data=wal_uav_df[,c(3:26,29,31,32)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
predict(lasso_uav_swp$finalModel, type='coef', mode="norm")$coefficients[10,]


lasso_uav_swpbs <- train(swp.bs~., data=wal_uav_df[,c(3:26,30,31,32)], method='lasso',trControl=fitControl, tuneLength=10, preProcess = c('center','scale'))
#the coefficients
predict(lasso_uav_swpbs$finalModel, type='coef', mode="norm")$coefficients[10,]

```


#rank features by importance from random forest
```{r}


#train with random forest regression model
$#model_rf_uav_1 <- train(x=X_uav_filter2, y=df_uav$swp, method = "rf", preProcess = c("scale","center"), trControl = control_uav, importance = TRUE, tuneLength = 10)
model_rf_uav <- train(x=wal_uav_df[,c(3:26,31,32)], y=df_uav$swp, method = "rf", preProcess = c("scale","center"), trControl = control_uav, importance = TRUE, tuneLength = 10)

model_rf_uav_swpbs <- train(x=wal_uav_df[,c(3:26,31,32)], y=df_uav$swp.bs, method = "rf", preProcess = c("scale","center"), trControl = control_uav, importance = TRUE, tuneLength = 10)


model_rf_uav
importance_rf_uav <- varImp(model_rf_uav)
importance_rf_uav

model_rf_uav_total <- train(x=X_uav_filter1, y=df_uav$swp, method = "rf", preProcess = "scale", trControl = control_uav, importance = TRUE)

model_rf_uav
model_rf_uav_total
varImp(model_rf_uav)
varImp(model_rf_uav_total)
```

#before running the classification 
```{r}
swp.max = max(wal_uav_df$swp)
swp.min = min(wal_uav_df$swp)
swp.max
swp.min
swp_classification <- function(swp){
  swp_class <- cut(swp, breaks = c(swp.max, -4, -6, -8, -14),  labels = 4:1)
  return(swp_class)
}

swp_classification.2 <- function(swp){
  swp_class <- cut(swp, breaks = c(swp.max, -4, -6, -14), labels = 3:1)
  return(swp_class)
}


```

```{r}
model_rf.class_uav <- train(x=wal_uav_df[,c(3:26,31,32)], y=swp_classification(wal_uav_df$swp), method = "rf", preProcess = c("center","scale"), trControl = control_uav, importance = TRUE)
model_rf.class2_uav <- train(x=wal_uav_df[,c(3:26,31,32)], y=swp_classification.2(wal_uav_df$swp), method = "rf", preProcess = c("center","scale"), trControl = control_uav, importance = TRUE)

varImp(model_rf.class_uav)
varImp(model_rf.class2_uav)

confusionMatrix(model_rf.class_uav)
confusionMatrix(model_rf.class2_uav)

model_rf.class_uav_total <- train(x=X_uav_filter1, y=swp_classification(df_uav$swp), method = "rf", preProcess = "scale", trControl = control_uav, importance = TRUE)

model_rf.class2_uav <- train(x=X_uav_filter2, y=swp_classification.2(df_uav$swp), method = "rf", preProcess = "scale", trControl = control_uav, importance = TRUE)

model_rf.class2_uav_total <- train(x=X_uav_filter1, y=swp_classification.2(df_uav$swp), method = "rf", preProcess = "scale", trControl = control_uav, importance = TRUE)

model_rf.class_uav
model_rf.class_uav_total
varImp(model_rf.class_uav)
varImp(model_rf.class_uav_total)

confusionMatrix(model_rf.class_uav)
confusionMatrix(model_rf.class_uav_total)
confusionMatrix(model_rf.class2_uav)
confusionMatrix(model_rf.class2_uav_total)
```


```{r}
ggplot(data=df_uav, aes(x=re.ndwi,y=swp))+geom_point()
ggplot(data=df_uav, aes(x=re.ndwi, y=swp))+geom_point(aes(color=factor(date)))
ggplot(data=df_uav, aes(x=grvi1, y=swp))+geom_point(aes(color=factor(date)))
ggplot(data=df_uav, aes(x=psri.nir, y=swp))+geom_point(aes(color=factor(date)))

```

```{r}
df_uav$swp.class <- swp_classification(df_uav$swp)
summary(df_uav$swp.class)
```

